---
title: "Plot and analysis"
output: html_notebook
---

In this notebook, we analyze whether species richness and chain motives modulate the relationship between FCL and three enviornmental factors (resource availability, disturbances, and ecosystem sizes).
As we provide summary csv file for the database, one can skip
```{r Processing Cohen database}
library(tidyverse)
library(igraph)
library(Matrix)
FCLmean=function(A){
  # A: an adjacency matrix of directed food web
  N = nrow(A) # number of species in the food web
  # Check/Convert weighted matrix
  if(any(colSums(A)>1)){
    for(i in 1:N){
      if (sum(A[, i])>0){
        A[,i]=A[,i]/sum(A[, i])
      }
    }
  }
  if (rankMatrix(t(A-diag(N)))<N){
    # Then, we CANNNOT calculate either trophic levels or FCL in the food web 
    return (NaN)
  }else{
    # We can find unique trophic levels and FCL from the following linear equation
    TL=solve(t(A-diag(N)), rep(-1, N))
    
  return (max(TL)-1) # FCL= max TL -1
  }
}

FCL=function(A, def=-1){
  # A: an adjacency matrix of directed food web
  # def: definition of FCL. We choose one definition from below
  # def =-1: shortest-path
  # def = 1: longest-path. Only acyclic graph
  
  N = nrow(A) # number of species in the food web
  TL=rep(0, N)
  B=c()
  # Check the indexes of basal species
  for (i in 1:N){
    if (sum(A[, i])==0){
      TL[i]=1 # basal species
      B=c(B, i) # list of basal species
    }
  }
  
  # Check whether A is DAG or not
  # calculate trophic levels 
  
  
  for (i in 1:N){
    if(TL[i]==0){
      # analyze nob-basal species
      if (def==0){
          # we define FCL by mean prey's tropic level
          TL[i] = 1+(TL[1:(i-1)]%*%A[1:(i-1), i])/sum(A[1:(i-1), i])
      }
      else if (def==-1){
          # TL of species i is defined by 1+the shortest path from a basal species
          graph=graph_from_adjacency_matrix(A,mode='directed')
          TL[i] = 1+min(distances(graph,to = i, mode='out')[B]) 
      }
      else if (def==1){
          #TL of species i is defined by 1+the longest path from a basal species
          # Because igraph does not have an algorithm for the longest path
          # we will use the shortest path with negative weights
          graph=graph_from_adjacency_matrix(-A,mode='directed', weight=TRUE)
          TL[i] =1- min(distances(graph,to = i, mode='out')[B]) # we only care distances from basal species to species i
      }
    }
  }
 #print(TL)
  return (max(TL)-1) # FCL= max TL -1
}
# define A 

# read from Data base
Analysis = function (d){
  # d row csv file
  # return FCLs and number fo the motives
  D=d[, 4:ncol(d)] # because of separaters of the file, we have empty two cols, Third col represents id of preys
  #rownames(D)=d[, 3]
  #colnames(D)=d[1,4:ncol(d) ]
  A=data.frame(D)
  colnames(A)=colnames(D)
  rownames(A)=as.character(unlist(d[, 3]))
  for (i in 1:nrow(A)){
    if (as.integer(rownames(A))[i]<10){
      rownames(A)[i] = paste0("0",rownames(A)[i])
    }
  }
  
  for (i in 1:ncol(A)){
    if (as.integer(colnames(A))[i]<10){
      colnames(A)[i] = paste0("0",colnames(A)[i])
    }
  }
  # We need to convert a data into NxN matrix
  N_list=sort(unique(c(rownames(A), colnames(A)))) # total number of species in the food web
  col_check=!(N_list %in% colnames(A)) # which species is missing in columns?
  row_check=!(N_list %in% rownames(A)) # which species is missing in rows?
  for(i in 1:length(N_list)){
    if (col_check[i]==TRUE){
       add = rep(0, nrow(A))
       a=cbind(A, add)
       #if(i<10){
       #  colnames(a)=c(colnames(A), paste0("0",N_list[0]))
       #}else{
        # colnames(a)=c(colnames(A), paste0(N_list[i]))
       #}
       colnames(a)=c(colnames(A), paste0(N_list[i]))
       A= a %>% select(all_of(names(a) %>% sort())) # update A and sorting
    }
    if (row_check[i]==TRUE){
       add = rep(0, ncol(A))
       a=rbind(A, add)
       #if(i<10){
      #   rownames(a)=c(rownames(A), paste0("0",N_list[i]))
      # }else{
       #  rownames(a)=c(rownames(A), paste0(N_list[i]))
       #}
       rownames(a)=c(rownames(A), paste0(N_list[i]))
       A=a %>% arrange(rownames(a)) # update A and sorting
    }
  } 
  A=matrix(unlist(A), ncol=ncol(A))  # convert matrix so that we can use it in igraph
  graph=graph_from_adjacency_matrix(A,mode='directed')
  if (is.dag(graph)==TRUE){
  FCL_mean=FCLmean(A) # FCL based on mean prey trophic level
    # convert weighted adj into unweighted one
    A =matrix(as.integer(A>0), nrow=nrow(A))
    FCL_long = FCL(A, 1)
  }else{
  # In this case, two FCLs cannot be defined
  FCL_mean=FCLmean(A)
  FCL_long=NaN
  # convert weighted adj into unweighted one
  A =matrix(as.integer(A>0), nrow=nrow(A))
  }
  FCL_short =FCL(A, -1) # this can be defined in any food webs. Return Inf without basal species
  
  motif=matrix(triad_census(graph), nrow=1)
  # the names of the motives follow previous studies
  data=data.frame(FCL_short, FCL_mean, FCL_long, nrow(A), motif)
  colnames(data) = c('FCL_short', 'FCL_mean', 'FCL_long',"richness", 
                    "empty","monoA-single","bi-single",
                    "s5","s4","s1","d4","d3","s2",
                    "s3","d8","d2","d1","d5","d7","d6")
  return (data)
}
#---------------MAIN-----------------------------
for(i in 1:213){
  fname=paste0('./EmpiricalFoodWeb/ECOWeB1.1/DATFILES Predation Matrices/WEB',i,'.DAT') # path of the files
  d=read_csv(fname)
  if (i==1){
  data=Analysis(d)
  }else{
    data=rbind(data, Analysis(d))
  }
write.csv(data, "Cohen2010_summary.csv", row.names = FALSE)
}
  
```
Now we analyze the data.
First, we investigate whether species richness and food web motives correlate with FCL or not.
```{r Read csv data}
library(ggplot2)
library(patchwork)
library(tidyverse)

df_emp=read.csv("Cohen2010_summary.csv") # empirical data
df_long=read.csv("./Simulations/FCL_long_simulations_summary.csv") # simulation using FCL long
df_mean=read.csv("./Simulations/FCL_mean_simulations_summary.csv") # simulation using FCL mean
df_short=read.csv("./Simulations/FCL_short_simulations_summary.csv") # simulation using FCL short

# Preparing data analysis
# For df_emp, we removed unnecessary columns and convert the count data of motives into fractions
df_emp = subset(df_emp, select = -c(empty,monoA.single, bi.single) )
df_emp=df_emp %>% select(order(colnames(df_emp)))
df_emp=dplyr::select(df_emp, WEB_id,Ecosystem, FCL_long,FCL_mean, FCL_short,richness,Ecosystem, everything())
sum.motif=apply(df_emp[, 7:ncol(df_emp)], 1, sum) # sum of motives in each row
df_emp[, 7:ncol(df_emp)] = df_emp[, 7:ncol(df_emp)]/sum.motif # converting into fractions of motives
# we remove motives that do not  or rarely appear
df_emp = subset(df_emp, select = -c(WEB_id, d1, d2,d3, d4, s3, d5, d6, d7,d8) )
colnames(df_emp) = c('Ecosystems', 'FCL_long', 'FCL_mean', 'FCL_short', 'Richness', 
                 'Chain', 'Omnivory', 'Apparent', 'Exploitative')
```
Next we plot FCL against the richness and motives 

```{r Empirical richness and motives}
r1=ggplot(df_emp, aes(x=Richness, y=FCL_long, size=4, alpha=0.5))+geom_point(color='black')+ylab('FCL long')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+annotate(geom="text", x=40, y=9, label=paste0('corr.=', round(cor.test(na.omit(df_emp)$FCL_long, na.omit(df_emp)$Richness, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(na.omit(df_emp)$FCL_long, na.omit(df_emp)$Richness, method='spearman')$p.value, 3)), size=5)
# Note df_emp$FCL_long includes some NA because of cyclic food webs
r2=ggplot(df_emp, aes(x=Richness, y=FCL_mean, size=4, alpha=0.5))+geom_point(color='black')+ylab('FCL mean')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+annotate(geom="text", x=40, y=4.5, label=paste0('corr.=', round(cor.test(df_emp$FCL_mean, df_emp$Richness, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df_emp$FCL_mean, df_emp$Richness, method='spearman')$p.value, 3)), size=5)

r3=ggplot(df_emp, aes(x=Richness, y=FCL_short, size=4, alpha=0.5))+geom_point(color='black')+ylab('FCL short')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+annotate(geom="text", x=40, y=3.75, label=paste0('corr.=', round(cor.test(df_emp$FCL_short, df_emp$Richness, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df_emp$FCL_short, df_emp$Richness, method='spearman')$p.value, 3)), size=5)

m1=ggplot(df_emp, aes(x=Chain, y=FCL_long, size=4, alpha=0.5))+geom_point(color='#a6cee3')+ylab('FCL long')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=9, label=paste0('corr.=', round(cor.test(df_emp$FCL_long, df_emp$Chain, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df_emp$FCL_long, df_emp$Chain, method='spearman')$p.value, 3)), size=5)

m2=ggplot(df_emp, aes(x=Omnivory, y=FCL_long, size=4, alpha=0.5))+geom_point(color='#1f78b4')+ylab('FCL long')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )  +xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=9, label=paste0('corr.=', round(cor.test(df_emp$FCL_long, df_emp$Omnivory, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df_emp$FCL_long, df_emp$Omnivory, method='spearman')$p.value, 3)), size=5)

m3=ggplot(df_emp, aes(x=Apparent, y=FCL_long, size=4, alpha=0.5))+geom_point(color='#b2df8a')+ylab('FCL long')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=9, label=paste0('corr.=', round(cor.test(df_emp$FCL_long, df_emp$Apparent, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df_emp$FCL_long, df_emp$Apparent, method='spearman')$p.value, 3)), size=5)

m4=ggplot(df_emp, aes(x=Exploitative, y=FCL_long, size=4, alpha=0.5))+geom_point(color='#33a02c')+ylab('FCL long')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=9, label=paste0('corr.=', round(cor.test(df_emp$FCL_long, df_emp$Exploitative, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df_emp$FCL_long, df_emp$Exploitative, method='spearman')$p.value, 3)), size=5)


m5=ggplot(df_emp, aes(x=Chain, y=FCL_mean, size=4, alpha=0.5))+geom_point(color='#a6cee3')+ylab('FCL mean')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=4.5, label=paste0('corr.=', round(cor.test(df_emp$FCL_mean, df_emp$Chain, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df_emp$FCL_mean, df_emp$Chain, method='spearman')$p.value, 3)), size=5)

m6=ggplot(df_emp, aes(x=Omnivory, y=FCL_mean, size=4, alpha=0.5))+geom_point(color='#1f78b4')+ylab('FCL mean')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )  +xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=4.5, label=paste0('corr.=', round(cor.test(df_emp$FCL_mean, df_emp$Omnivory, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df_emp$FCL_mean, df_emp$Omnivory, method='spearman')$p.value, 3)), size=5)

m7=ggplot(df_emp, aes(x=Apparent, y=FCL_mean, size=4, alpha=0.5))+geom_point(color='#b2df8a')+ylab('FCL short')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=4.5, label=paste0('corr.=', round(cor.test(df_emp$FCL_mean, df_emp$Apparent, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df_emp$FCL_mean, df_emp$Apparent, method='spearman')$p.value, 3)), size=5)

m8=ggplot(df_emp, aes(x=Exploitative, y=FCL_mean, size=4, alpha=0.5))+geom_point(color='#33a02c')+ylab('FCL short')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=4.5, label=paste0('corr.=', round(cor.test(df_emp$FCL_mean, df_emp$Exploitative, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df_emp$FCL_mean, df_emp$Exploitative, method='spearman')$p.value, 3)), size=5)

m9=ggplot(df_emp, aes(x=Chain, y=FCL_short, size=4, alpha=0.5))+geom_point(color='#a6cee3')+ylab('FCL short')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=3.75, label=paste0('corr.=', round(cor.test(df_emp$FCL_short, df_emp$Chain, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df_emp$FCL_short, df_emp$Chain, method='spearman')$p.value, 3)), size=5)

m10=ggplot(df_emp, aes(x=Omnivory, y=FCL_short, size=4, alpha=0.5))+geom_point(color='#1f78b4')+ylab('FCL short')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )  +xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=3.75, label=paste0('corr.=', round(cor.test(df_emp$FCL_short, df_emp$Omnivory, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df_emp$FCL_short, df_emp$Omnivory, method='spearman')$p.value, 3)), size=5)

m11=ggplot(df_emp, aes(x=Apparent, y=FCL_short, size=4, alpha=0.5))+geom_point(color='#b2df8a')+ylab('FCL short')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=3.75, label=paste0('corr.=', round(cor.test(df_emp$FCL_short, df_emp$Apparent, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df_emp$FCL_short, df_emp$Apparent, method='spearman')$p.value, 3)), size=5)

m12=ggplot(df_emp, aes(x=Exploitative, y=FCL_short, size=4, alpha=0.5))+geom_point(color='#33a02c')+ylab('FCL short')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=3.75, label=paste0('corr.=', round(cor.test(df_emp$FCL_short, df_emp$Exploitative, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df_emp$FCL_short, df_emp$Exploitative, method='spearman')$p.value, 3)), size=5)

g=r1+r2+r3+m1+m5+m9+m2+m6+m10+m3+m7+m11+m4+m8+m12+plot_layout(nrow = 5, ncol=3)+plot_annotation(tag_levels = "A")&theme(plot.tag = element_text(size = 32))

ggsave('./empirical_pdf/FCL_empirical.pdf', width=12, height=12)
```

```{r Simulated richness and motives}
# Note: if richness =0 or 1 => motives cannot be defined and correponding data are removed 
r1=ggplot(df_long, aes(x=richness, y=FCL, size=3, alpha=0.005))+geom_point(color='black')+ylab('FCL long')+xlab("Richness")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+annotate(geom="text", x=10, y=11, label=paste0('corr.=', round(cor.test(df_long$FCL, df_long$richness, method='spearman')$estimate, 3)), size=5)
r2=ggplot(df_mean, aes(x=richness, y=FCL, size=3, alpha=0.005))+geom_point(color='black')+ylab('FCL mean')+xlab("Richness")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+annotate(geom="text", x=10, y=9, label=paste0('corr.=', round(cor.test(df_mean$FCL, df_mean$richness, method='spearman')$estimate, 3)), size=5)
r3=ggplot(df_short, aes(x=richness, y=FCL, size=3, alpha=0.005))+geom_point(color='black')+ylab('FCL short')+xlab("Richness")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+annotate(geom="text", x=10, y=9, label=paste0('corr.=', round(cor.test(df_short$FCL, df_short$richness, method='spearman')$estimate, 3)), size=5)

m1=ggplot(df_long, aes(x=chain, y=FCL, size=4, alpha=0.1))+geom_point(color='#a6cee3')+ylab('FCL long')+xlab("Chain")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=11, label=paste0('corr.=', round(cor.test(df_long$FCL, df_long$chain, method='spearman')$estimate, 3)), size=5)

m2=ggplot(df_long, aes(x=omnivory, y=FCL, size=4, alpha=0.1))+geom_point(color='#1f78b4')+ylab('FCL long')+xlab("Omnivory")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=11, label=paste0('corr.=', round(cor.test(df_long$FCL, df_long$omnivory, method='spearman')$estimate, 3)), size=5)

m3=ggplot(df_long, aes(x=apparent, y=FCL, size=4, alpha=0.1))+geom_point(color='#b2df8a')+ylab('FCL long')+xlab("Apparent")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=11, label=paste0('corr.=', round(cor.test(df_long$FCL, df_long$apparent, method='spearman')$estimate, 3)), size=5)

m4=ggplot(df_long, aes(x=exploitative, y=FCL, size=4, alpha=0.1))+geom_point(color='#33a02c')+ylab('FCL long')+xlab("Exploitative")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=11, label=paste0('corr.=', round(cor.test(df_long$FCL, df_long$exploitative, method='spearman')$estimate, 3)), size=5)


m5=ggplot(df_mean, aes(x=chain, y=FCL, size=4, alpha=0.1))+geom_point(color='#a6cee3')+ylab('FCL mean')+xlab("Chain")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=9, label=paste0('corr.=', round(cor.test(df_mean$FCL, df_mean$chain, method='spearman')$estimate, 3)), size=5)

m6=ggplot(df_mean, aes(x=omnivory, y=FCL, size=4, alpha=0.1))+geom_point(color='#1f78b4')+ylab('FCL mean')+xlab("Omnivory")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=9, label=paste0('corr.=', round(cor.test(df_mean$FCL, df_mean$omnivory, method='spearman')$estimate, 3)), size=5)

m7=ggplot(df_mean, aes(x=apparent, y=FCL, size=4, alpha=0.1))+geom_point(color='#b2df8a')+ylab('FCL mean')+xlab("Apparent")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=9, label=paste0('corr.=', round(cor.test(df_mean$FCL, df_mean$apparent, method='spearman')$estimate, 3)), size=5)

m8=ggplot(df_mean, aes(x=exploitative, y=FCL, size=4, alpha=0.1))+geom_point(color='#33a02c')+ylab('FCL mean')+xlab("Exploitative")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=9, label=paste0('corr.=', round(cor.test(df_mean$FCL, df_mean$exploitative, method='spearman')$estimate, 3)), size=5)

m9=ggplot(df_short, aes(x=chain, y=FCL, size=4, alpha=0.1))+geom_point(color='#a6cee3')+ylab('FCL short')+xlab("Chain")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=9, label=paste0('corr.=', round(cor.test(df_short$FCL, df_short$chain, method='spearman')$estimate, 3)), size=5)

m10=ggplot(df_short, aes(x=omnivory, y=FCL, size=4, alpha=0.1))+geom_point(color='#1f78b4')+ylab('FCL short')+xlab("Omnivory")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=9, label=paste0('corr.=', round(cor.test(df_short$FCL, df_short$omnivory, method='spearman')$estimate, 3)), size=5)

m11=ggplot(df_short, aes(x=apparent, y=FCL, size=4, alpha=0.1))+geom_point(color='#b2df8a')+ylab('FCL short')+xlab("Apparent")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=9, label=paste0('corr.=', round(cor.test(df_short$FCL, df_short$apparent, method='spearman')$estimate, 3)), size=5)

m12=ggplot(df_short, aes(x=exploitative, y=FCL, size=4, alpha=0.1))+geom_point(color='#33a02c')+ylab('FCL short')+xlab("Exploitative")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=9, label=paste0('corr.=', round(cor.test(df_short$FCL, df_short$exploitative, method='spearman')$estimate, 3)), size=5)

r1+r2+r3+m1+m5+m9+m2+m6+m10+m3+m7+m11+m4+m8+m12+plot_layout(nrow = 5, ncol=3)+plot_annotation(tag_levels = "A")&theme(plot.tag = element_text(size = 32))
ggsave('./Simulations/simulation_pdf/FCL_simulation_correlation.png', width=12, height=16)

```

Next, we analyze how species richness and food web motives affect FCL.
We assume three functional responses: linear, saturating, or quadratic.
We calculate the Akaike Information criterion of 15 models given FCL 
in empirical data set or simulation data.

```{r Model selection in empirical data}
b_start=0.5 # need to tune initial guess so that the algortihm works
AIC_cal2= function(df){
  #-------------Model description------------------------
  model1=nls(formula = FCL + 1 ~ a*Richness, data = df, algorithm='port', 
             lower=c(a=0), upper=c(a=max(df$FCL)+1), start=c(a=1))
  model2=nls(FCL ~ a*(1-exp(-b*Richness))-1, data=df, start=c(a=max(df$FCL)/2, b=b_start),  
             algorithm='port', lower=c(a=0, b=0), upper=c(a=max(df$FCL)+1, b =10)) # saturating func of richness
  model3=nls(FCL ~ -a*Richness^2+b*Richness-1, data=df, start=c(a=1, b=1), 
             algorithm='port', lower=c(a=0, b=0), upper=c(a=10, b=10)) # quadratic func of richness
  model4=nls(formula = FCL + 1 ~ a*Chain, data = df,
             algorithm='port', lower=c(a=0), upper=c(a=max(df$FCL)+1), start=c(a=1))# linear func of chain
  model5=nls(FCL ~ a*(1-exp(-b*Chain))-1, data=df, start=c(a=max(df$FCL)/2, b=b_start),  
             algorithm='port', lower=c(a=0, b=0), upper=c(a=max(df$FCL)+1, b=10)) # saturating func of chain
  model6=nls(FCL ~ -a*Chain^2+b*Chain-1, data=df, start=c(a=1, b=1), 
             algorithm='port', lower=c(a=0, b=0), upper=c(a=10, b=10)) # quadratic func of chain
 
  #combination of chain and richness
  model14=nls(formula = FCL + 1 ~ a*Richness+b*Chain,  lower=c(a=0, b=0), algorithm='port', upper=c(a=max(df$FCL)+1, b=max(df$FCL)+1), 
              start=c(a=1, b=1), data = df)# linear func of chain
  model15=nls(FCL ~ a*Richness+b*(1-exp(-c*Chain))-1, data=df, start=c(a=0.1, b=max(df$FCL)/2, c=b_start), 
              algorithm='port', lower=c(a=0, b=0, c=0), upper=c(a=10, b=max(df$FCL)+1, c=10))
  model16=nls(FCL ~ a*Richness-b*Chain^2+c*Chain-1, data=df, start=c(a=0.1, b=1, c=1), 
              algorithm='port', lower=c(a=0, b=0, c=0), upper=c(a=10, b=10, c=10))
  model24=nls(FCL ~ a*(1-exp(-b*Richness))+c*Chain-1, data=df, start=c(a=max(df$FCL)/2, b=b_start, c=1),
              algorithm='port', lower=c(a=0, b=0, c=0), upper=c(a=max(df$FCL)+1, b=10, c=10))
  model25=nls(FCL ~ a*(1-exp(-b*Richness))+c*(1-exp(-d*Chain))-1, data=df, 
              start=c(a=max(df$FCL)/2, b=b_start, c=max(df$FCL)/2, d=b_start), 
              algorithm='port', lower=c(a=0, b=0, c=0, d=0),
              upper=c(a=max(df$FCL)+1, b=10, c=max(df$FCL)+1, d=10))
  model26=nls(FCL ~ a*(1-exp(-b*Richness))-c*Chain^2+d*Chain-1, data=df, 
              start=c(a=max(df$FCL)/2, b=b_start, c=1, d=1.05), # d= 1 cause a problem of conversence
              algorithm='port', lower=c(a=0, b=0, c=0, d=0), 
              upper=c(a=max(df$FCL)+1, b=10, c=10, d=10))
  model34=nls(FCL ~ -a*Richness^2+b*Richness+c*Chain-1, data=df, start=c(a=1, b=1, c=1),
              algorithm='port', lower=c(a=0, b=0, c=0),
              upper=c(a=10, b=10, c=10))
  model35=nls(FCL ~ -a*Richness^2+b*Richness+c*(1-exp(-d*Chain))-1, data=df, 
              start=c(a=1, b=1, c=max(df$FCL)/2, d=b_start), 
              algorithm='port', lower=c(a=0, b=0, c=0, d=0), 
              upper=c(a=10, b=10, c=max(df$FCL)+1, d=10))
  model36=nls(FCL ~ -a*Richness^2+b*Richness-c*Chain^2+d*Chain-1, data=df, 
              start=c(a=1, b=1, c=1, d=1),
              algorithm='port', lower=c(a=0, b =0, c=0, d=0), 
              upper=c(a=10, b=10, c=10, d=10))
  
  AICs=c(AIC(model1), AIC(model2), AIC(model3), AIC(model4), AIC(model5), AIC(model6),
         AIC(model14),AIC(model15), AIC(model16), AIC(model24), AIC(model25), AIC(model26),
         AIC(model34),AIC(model35), AIC(model36))
  minAIC=min(AICs)
  deltaAIC=AICs-minAIC
  print(AICs)
  
  print(minAIC)
  
  print(deltaAIC)
  
  #print(summary(models[which.max(deltaAIC)]))
}

df_emp$FCL=df_emp$FCL_long
#FCL long
AIC_cal2(na.omit(df_emp)) # we omit FCL na in cyclic food webs
#FCL_mean
df_emp$FCL=df_emp$FCL_mean
AIC_cal2(df_emp)
#FCL short
df_emp$FCL=df_emp$FCL_short
AIC_cal2(df_emp)
```
The best models are saturating + quadriatic (in FCL long) or saturating + linear (in FCL short). However, in the FCL short, using saturating or quadratic functions in chain also seem fine. 
Below, we show the coefficnet values in the best models and plot them.

```{r Best models in mepirical data}
# FCL_long
summary(nls(FCL_long ~ a*(1-exp(-b*Richness))-c*Chain^2+d*Chain-1, data=na.omit(df_emp), 
              start=c(a=max(na.omit(df_emp)$FCL_long)/2, b=b_start, c=1, d=1.05), # d= 1 cause a problem of conversence
              algorithm='port', lower=c(a=0, b=0, c=0, d=0), 
              upper=c(a=max(na.omit(df_emp)$FCL_long)+1, b=10, c=10, d=10)))
#FCL mean
summary(nls(FCL_mean ~ a*(1-exp(-b*Richness))-c*Chain^2+d*Chain-1, data=na.omit(df_emp), 
              start=c(a=max(na.omit(df_emp)$FCL_mean)/2, b=b_start, c=1, d=1.0), 
              algorithm='port', lower=c(a=0, b=0, c=0, d=0), 
              upper=c(a=max(na.omit(df_emp)$FCL_mean)+1, b=10, c=10, d=10)))

# FCL short
summary(nls(FCL_short ~ a*(1-exp(-b*Richness))+c*Chain-1, data=df_emp, start=c(a=max(df_emp$FCL_short)/2, b=b_start, c=1),
              algorithm='port', lower=c(a=0, b=0, c=0), upper=c(a=max(df_emp$FCL_short)+1, b=10, c=10)))
```
```{r Plotting best models with empirical data}
df_emp$predict_short=2.85*(1-exp(-0.19*df_emp$Richness))+2.12*df_emp$Chain-1


g1=ggplot(df_emp, aes(x=Richness, y=FCL_short, size=3, alpha=0.000005))+geom_point(color='black')+ylab('FCL short')+xlab("Richness")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun = function(x) 2.85*(1-exp(-0.19*x))+2.12*mean(df_emp$Chain)-1, color='green')
g2=ggplot(df_emp, aes(x=Chain, y=FCL_short, size=3, alpha=0.000005))+geom_point(color='black')+ylab('FCL short')+xlab("Chain")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun = function(x) 2.85*(1-exp(-0.19*mean(df_emp$Richness)))+2.12*x-1, color='green')

g3=ggplot(df_emp, aes(x=FCL_short, y=predict_short, size=3, alpha=0.000005))+geom_point(color='black')+ylim(c(-1, 6))+xlab('FCL short')+ylab("Model prediction")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun=function(x) x, color='blue')

df_emp$predict_long=3.94*(1-exp(-0.09*df_emp$Richness))-7.3*df_emp$Chain^2+9.45*df_emp$Chain-1

g4=ggplot(df_emp, aes(x=Richness, y=FCL_long, size=3, alpha=0.000005))+geom_point(color='black')+ylab('FCL long')+xlab("Richness")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun = function(x) 3.94*(1-exp(-0.09*x))-7.3*mean(df_emp$Chain)^2+9.45*mean(df_emp$Chain)-1, color='green')
g5=ggplot(df_emp, aes(x=Chain, y=FCL_long, size=3, alpha=0.000005))+geom_point(color='black')+ylab('FCL long')+xlab("Chain")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun = function(x) 3.94*(1-exp(-0.09*mean(df_emp$Richness)))-7.3*x^2+9.45*x-1, color='green')
g6=ggplot(df_emp, aes(x=FCL_long, y=predict_long, size=3, alpha=0.000005))+geom_point(color='black')+ylim(c(-1, 6))+xlab('FCL long')+ylab("Model prediction")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun=function(x) x, color='blue')

df_emp$predict_mean=3.01*(1-exp(-0.14*df_emp$Richness))-2.82*df_emp$Chain^2+4.92*df_emp$Chain-1

g7=ggplot(df_emp, aes(x=Richness, y=FCL_mean, size=3, alpha=0.000005))+geom_point(color='black')+ylab('FCL mean')+xlab("Richness")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun = function(x) 3.01*(1-exp(-0.14*x))-2.82*mean(df_emp$Chain)^2+4.92*mean(df_emp$Chain)-1, color='green')
g8=ggplot(df_emp, aes(x=Chain, y=FCL_mean, size=3, alpha=0.000005))+geom_point(color='black')+ylab('FCL mean')+xlab("Chain")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun = function(x) 3.01*(1-exp(-0.14*mean(df_emp$Richness)))-2.82*x^2+4.92*x-1, color='green')
g9=ggplot(df_emp, aes(x=FCL_mean, y=predict_mean, size=3, alpha=0.000005))+geom_point(color='black')+ylim(c(-1, 5))+xlab('FCL mean')+ylab("Model prediction")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun=function(x) x, color='blue')
g4+g5+g6+g7+g8+g9+g1+g2+g3+plot_layout(nrow = 3)+plot_annotation(tag_levels = "A")&theme(plot.tag = element_text(size = 32))
ggsave('./empirical_pdf/Modeling_empirical.pdf', width=16, height=8)
```

```{r best models in simulaiton}
b_start=1.5 # need to tune initial guess so that the algortihm works
AIC_cal1= function(df, b_start=1.5){
    model1=nls(FCL ~ a*richness-1, data=df, start=c(a=1), algorithm='port', 
             lower=c(a=0), upper=c(a=10)) # linear func of richness
  model2=nls(FCL ~ a*(1-exp(-b*richness))-1, data=df, start=c(a=max(df$FCL)/2, b=b_start),  
             algorithm='port', lower=c(a=0, b=0), upper=c(a=max(df$FCL)+1, b =10)) # saturating func of richness
  model3=nls(FCL ~ -a*richness^2+b*richness-1, data=df, start=c(a=1, b=1), 
             algorithm='port', lower=c(a=0, b=0), upper=c(a=10, b=10)) # quadratic func of richness
  model4=nls(FCL ~ a*chain-1, data=df, start=c(a=1),  
             algorithm='port',lower=c(a=0), upper=(a=10)) # linear func of chain
  model5=nls(FCL ~ a*(1-exp(-b*chain))-1, data=df, start=c(a=max(df$FCL)/2, b=b_start),  
             algorithm='port', lower=c(a=0, b=0), upper=c(a=max(df$FCL)+1, b=10)) # saturating func of chain
  model6=nls(FCL ~ -a*chain^2+b*chain-1, data=df, start=c(a=1, b=1), 
             algorithm='port', lower=c(a=0, b=0), upper=c(a=10, b=10)) # quadratic func of chain
 
  #combination of chain and richness
  model14=nls(FCL ~ a*richness+b*chain-1, data=df, start=c(a=1, b=1), algorithm='port', 
              lower = c(a=0, b=0), upper=c(a=10, b=10))
  model15=nls(FCL ~ a*richness+b*(1-exp(-c*chain))-1, data=df, start=c(a=1, b=max(df$FCL)/2, c=b_start), 
              algorithm='port', lower=c(a=0, b=0, c=0), upper=c(a=10, b=max(df$FCL)+1, c=10))
  model16=nls(FCL ~ a*richness-b*chain^2+c*chain-1, data=df, start=c(a=1, b=1, c=1), 
              algorithm='port', lower=c(a=0, b=0, c=0), upper=c(a=10, b=10, c=10))
  model24=nls(FCL ~ a*(1-exp(-b*richness))+c*chain-1, data=df, start=c(a=max(df$FCL)/2, b=b_start, c=1),
              algorithm='port', lower=c(a=0, b=0, c=0), upper=c(a=max(df$FCL)+1, b=10, c=10), 
              control= nls.control(maxiter = 500))
  model25=nls(FCL ~ a*(1-exp(-b*richness))+c*(1-exp(-d*chain))-1, data=df, 
              start=c(a=max(df$FCL)/2, b=2*b_start, c=max(df$FCL)/2, d=2*b_start), 
              algorithm='port', lower=c(a=0, b=0, c=0, d=0),
              upper=c(a=max(df$FCL)+1, b=10, c=max(df$FCL)+1, d=10))
  model26=nls(FCL ~ a*(1-exp(-b*richness))-c*chain^2+d*chain-1, data=df, 
              start=c(a=max(df$FCL)/2, b=b_start, c=1, d=1), 
              algorithm='port', lower=c(a=0, b=0, c=0, d=0), 
              upper=c(a=max(df$FCL)+1, b=10, c=10, d=10))
  model34=nls(FCL ~ -a*richness^2+b*richness+c*chain-1, data=df, start=c(a=1, b=1, c=1),
              algorithm='port', lower=c(a=0, b=0, c=0),
              upper=c(a=10, b=10, c=10))
  model35=nls(FCL ~ -a*richness^2+b*richness+c*(1-exp(-d*chain))-1, data=df, 
              start=c(a=1, b=1, c=max(df$FCL)/2, d=b_start), 
              algorithm='port', lower=c(a=0, b=0, c=0, d=0), 
              upper=c(a=10, b=10, c=max(df$FCL)+1, d=10))
  model36=nls(FCL ~ -a*richness^2+b*richness-c*chain^2+d*chain-1, data=df, 
              start=c(a=1, b=1, c=1, d=1),
              algorithm='port', lower=c(a=0, b =0, c=0, d=0), 
              upper=c(a=10, b=10, c=10, d=10))
  
  AICs=c(AIC(model1), AIC(model2), AIC(model3), AIC(model4), AIC(model5), AIC(model6),
         AIC(model14),AIC(model15), AIC(model16), AIC(model24), AIC(model25), AIC(model26),
         AIC(model34),AIC(model35), AIC(model36))
   minAIC=min(AICs)
  deltaAIC=AICs-minAIC
  print(deltaAIC)
  print(minAIC)
}

#FCL long
AIC_cal1(df_long) 
#FCL mean
AIC_cal1(df_mean)
#FCL short
AIC_cal1(df_short, 2) # to avoid bad convergence

```

```{r the best models in simulation data}
model_long=nls(FCL ~ a*(1-exp(-b*richness))-c*chain^2+d*chain-1, data=df_long, 
              start=c(a=max(df_long$FCL)/2, b=b_start, c=1, d=1), 
              algorithm='port', lower=c(a=0, b=0, c=0, d=0), 
              upper=c(a=max(df_long$FCL)+1, b=10, c=10, d=10))
summary(model_long)

model_mean=nls(FCL ~ a*(1-exp(-b*richness))-c*chain^2+d*chain-1, data=df_mean, 
              start=c(a=max(df_mean$FCL)/2, b=b_start, c=1, d=1), 
              algorithm='port', lower=c(a=0, b=0, c=0, d=0), 
              upper=c(a=max(df_mean$FCL)+1, b=10, c=10, d=10))
summary(model_mean)

model_short=nls(FCL ~ a*(1-exp(-b*richness))-c*chain^2+d*chain-1, data=df_short, 
              start=c(a=max(df_short$FCL)/2, b=2, c=1, d=1), 
              algorithm='port', lower=c(a=0, b=0, c=0, d=0), 
              upper=c(a=max(df_short$FCL)+1, b=10, c=10, d=10))
summary(model_short)

```

```{r best models for simulation data}
# First we fill na with 0s (corresponding richness < 2)

df_long$predict=6.92*(1-exp(-0.08*df_long$richness))-1.49*replace(df_long,is.na(df_long),0)$chain^2+3.15*replace(df_long,is.na(df_long),0)$chain-1 # replace na with 0
g1=ggplot(df_long, aes(x=richness, y=FCL, size=3, alpha=0.000005))+geom_point(color='black')+ylab('FCL long')+xlab("Richness")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun = function(x) 6.92*(1-exp(-0.08*x))-1.49*mean(df_long$chain, na.rm=TRUE)^2+3.15*mean(df_long$chain, na.rm=TRUE)-1, color='green')
g2=ggplot(df_long, aes(x=chain, y=FCL, size=3, alpha=0.000005))+geom_point(color='black')+ylab('FCL long')+xlab("Chain")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun = function(x) 6.92*(1-exp(-0.08*mean(df_long$richness)))-1.49*x^2+3.15*x-1, color='green')
g3=ggplot(df_long, aes(x=FCL, y=predict, size=3, alpha=0.000005))+geom_point(color='black')+ylim(c(-1, 6))+xlab('FCL long')+ylab("Model prediction")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun=function(x) x, color='blue')

# FCL mean 
df_mean$predict=3.81*(1-exp(-0.17*df_mean$richness))-0.91*replace(df_mean,is.na(df_mean),0)$chain^2+2.43*replace(df_mean,is.na(df_mean),0)$chain-1
g4=ggplot(df_mean, aes(x=richness, y=FCL, size=3, alpha=0.000005))+geom_point(color='black')+ylab('FCL mean')+xlab("Richness")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun = function(x) 3.81*(1-exp(-0.17*x))-0.91*mean(df_mean$chain, na.rm=TRUE)^2+2.43*mean(df_mean$chain, na.rm=TRUE)-1, color='green')
g5=ggplot(df_mean, aes(x=chain, y=FCL, size=3, alpha=0.000005))+geom_point(color='black')+ylab('FCL mean')+xlab("Chain")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun = function(x) 3.81*(1-exp(-0.17*mean(df_mean$richness)))-0.91*x^2+2.43*x-1, color='green')
g6=ggplot(df_mean, aes(x=FCL, y=predict, size=3, alpha=0.000005))+geom_point(color='black')+ylim(c(-1, 6))+xlab('FCL mean')+ylab("Model prediction")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun=function(x) x, color='blue')

#FCL short
df_short$predict=2.98*(1-exp(-0.24*df_short$richness))-0.69*replace(df_short,is.na(df_short),0)$chain^2+2.13*replace(df_short,is.na(df_short),0)$chain-1
g7=ggplot(df_short, aes(x=richness, y=FCL, size=3, alpha=0.000005))+geom_point(color='black')+ylab('FCL short')+xlab("Richness")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun = function(x) 2.98*(1-exp(-0.24*x))-0.69*mean(df_short$chain, na.rm=TRUE)^2+2.13*mean(df_short$chain, na.rm=TRUE)-1, color='green')
g8=ggplot(df_short, aes(x=chain, y=FCL, size=3, alpha=0.000005))+geom_point(color='black')+ylab('FCL short')+xlab("Chain")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun = function(x) 2.98*(1-exp(-0.24*mean(df_short$richness)))-0.69*x^2+2.13*x-1, color='green')
g9=ggplot(df_short, aes(x=FCL, y=predict, size=3, alpha=0.000005))+geom_point(color='black')+ylim(c(-1, 6))+xlab('FCL short')+ylab("Model prediction")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun=function(x) x, color='blue')

g1+g2+g3+g4+g5+g6+g7+g8+g9+plot_layout(nrow = 3,)+plot_annotation(tag_levels = "A")&theme(plot.tag = element_text(size = 32))

ggsave('./Simulations/simulation_pdf/Modeling_simulations.png', width=12, height=8)

```

Now we show how the three environmental drivers relate to FCL, species richness and the chain motif.
First, we check the relationships between enviornments and FCL

```{r Eviornment vs FCL}
p1=ggplot(df_long, aes(x=factor(resource), y=FCL))+geom_violin(color='#7570b3')+ylab('FCL long')+xlab("Resource")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+annotate(geom="text", x=2, y=11, label=paste0('corr.=', round(cor.test(df_long$FCL, df_long$resource, method='spearman')$estimate, 3)), size=5)

p2=ggplot(df_long, aes(x=factor(disturbance), y=FCL))+geom_violin(color='#d95f02')+ylab('FCL long')+xlab("Disturbance")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+annotate(geom="text", x=1.5, y=11, label=paste0('corr.=', round(cor.test(df_long$FCL, df_long$disturbance, method='spearman')$estimate, 3)), size=5)

p3=ggplot(df_long, aes(x=factor(ecosystem), y=FCL))+geom_violin(color='#1b9e77')+ylab('FCL long')+xlab("Ecosystem")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+annotate(geom="text", x=1.5, y=11, label=paste0('corr.=', round(cor.test(df_long$FCL, df_long$ecosystem, method='spearman')$estimate, 3)), size=5)


p4=ggplot(df_mean, aes(x=factor(resource), y=FCL))+geom_violin(color='#7570b3')+ylab('FCL mean')+xlab("Resource")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+annotate(geom="text", x=2, y=9, label=paste0('corr.=', round(cor.test(df_mean$FCL, df_mean$resource, method='spearman')$estimate, 3)), size=5)

p5=ggplot(df_mean, aes(x=factor(disturbance), y=FCL))+geom_violin(color='#d95f02')+ylab('FCL mean')+xlab("Disturbance")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+annotate(geom="text", x=1.5, y=9, label=paste0('corr.=', round(cor.test(df_mean$FCL, df_mean$disturbance, method='spearman')$estimate, 3)), size=5)

p6=ggplot(df_mean, aes(x=factor(ecosystem), y=FCL))+geom_violin(color='#1b9e77')+ylab('FCL mean')+xlab("Ecosystem")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+annotate(geom="text", x=1.5, y=9, label=paste0('corr.=', round(cor.test(df_mean$FCL, df_mean$ecosystem, method='spearman')$estimate, 3)), size=5)


p7=ggplot(df_short, aes(x=factor(resource), y=FCL))+geom_violin(color='#7570b3')+ylab('FCL short')+xlab("Resource")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+annotate(geom="text", x=2, y=9, label=paste0('corr.=', round(cor.test(df_short$FCL, df_short$resource, method='spearman')$estimate, 3)), size=5)

p8=ggplot(df_short, aes(x=factor(disturbance), y=FCL))+geom_violin(color='#d95f02')+ylab('FCL short')+xlab("Disturbance")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+annotate(geom="text", x=1.5, y=9, label=paste0('corr.=', round(cor.test(df_short$FCL, df_short$disturbance, method='spearman')$estimate, 3)), size=5)

p9=ggplot(df_short, aes(x=factor(ecosystem), y=FCL))+geom_violin(color='#1b9e77')+ylab('FCL short')+xlab("Ecosystem")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+annotate(geom="text", x=1.5, y=9, label=paste0('corr.=', round(cor.test(df_short$FCL, df_short$ecosystem, method='spearman')$estimate, 3)), size=5)

p1+p4+p7+p2+p5+p8+p3+p6+p9+plot_layout(nrow = 3,)+plot_annotation(tag_levels = "A")&theme(plot.tag = element_text(size = 32))
ggsave('./Simulations/simulation_pdf/FCL_simulation_environemnt.pdf', width=12, height=9)
```
Next we plot richness and chain over the environments.
We plot three figures for each definition of FCL
```{r modulater and enviornments}
PlotCumulative =function(df, fname){
  g1=ggplot(df, aes(richness, linetype=factor(resource)))+ stat_ecdf(geom = "step", color='#7570b3')
  g1=g1+xlab('Richness')+ylab('Cumulative Prob.')  
  g1=g1+xlim(c(0, 32))+theme(
  axis.text.x = element_text(size=14),
    axis.title.x = element_text(size=20),
     axis.text.y = element_text(size=14),
    axis.title.y = element_text(size=20),
    legend.position = 'none')+labs(linetype = "Resource")
  
  
  g2=ggplot(df, aes(richness, linetype=factor(disturbance)))+ stat_ecdf(geom = "step", color='#d95f02')
  g2=g2+xlab('Richness')+ylab('Cumulative Prob.')  
  g2=g2+xlim(c(0, 32))+theme(
  axis.text.x = element_text(size=14),
    axis.title.x = element_text(size=20),
     axis.text.y = element_text(size=14),
    axis.title.y = element_text(size=20),
    legend.position = 'none')+labs(linetype = "Disturbance")
  
  g3=ggplot(df, aes(richness, linetype=factor(ecosystem)))+ stat_ecdf(geom = "step", color='#1b9e77')
  g3=g3+xlab('Richness')+ylab('Cumulative Prob.')  
  g3=g3+xlim(c(0, 32))+theme(
  axis.text.x = element_text(size=14),
    axis.title.x = element_text(size=20),
     axis.text.y = element_text(size=14),
    axis.title.y = element_text(size=20),
    legend.position = 'none')+labs(linetype = "Ecosystem")
  
  g4=ggplot(df, aes(chain, linetype=factor(resource)))+ stat_ecdf(geom = "step", color='#7570b3')
  g4=g4+xlab('Chain')+ylab('Cumulative Prob.')  
  g4=g4+xlim(c(0, 1))+theme(
  axis.text.x = element_text(size=14),
    axis.title.x = element_text(size=20),
     axis.text.y = element_text(size=14),
    axis.title.y = element_text(size=20),
    legend.title=element_text(size=20),
  legend.text=element_text(size=14))+labs(linetype = "Resource")
  
  
  g5=ggplot(df, aes(chain, linetype=factor(disturbance)))+ stat_ecdf(geom = "step", color='#d95f02')
  g5=g5+xlab('Chain')+ylab('Cumulative Prob.')  
  g5=g5+xlim(c(0, 1))+theme(
  axis.text.x = element_text(size=14),
    axis.title.x = element_text(size=20),
     axis.text.y = element_text(size=14),
    axis.title.y = element_text(size=20),
    legend.title=element_text(size=20),
  legend.text=element_text(size=14))+labs(linetype = "Disturbance")
  
  g6=ggplot(df, aes(chain, linetype=factor(ecosystem)))+ stat_ecdf(geom = "step", color='#1b9e77')
  g6=g6+xlab('Chain')+ylab('Cumulative Prob.')  
  g6=g6+xlim(c(0, 1))+theme(
  axis.text.x = element_text(size=14),
    axis.title.x = element_text(size=20),
     axis.text.y = element_text(size=14),
    axis.title.y = element_text(size=20),
    legend.title=element_text(size=20),
  legend.text=element_text(size=14))+labs(linetype = "Ecosystem")
  
  g1+g4+g2+g5+g3+g6+plot_layout(nrow = 3,)+plot_annotation(tag_levels = "A")&theme(plot.tag = element_text(size = 32))
  ggsave(paste0('./Simulations/simulation_pdf/', fname), heigh=12, width=12)
}
PlotCumulative(df_long,'Cumulative_richness_chain_FCLlong.pdf')
PlotCumulative(df_mean,'Cumulative_richness_chain_FCLmean.pdf')
PlotCumulative(df_short,'Cumulative_richness_chain_FCLshort.pdf')
```

Below, we plot some additional data.
First, we categorized the ecosystems from the empirical data base.
```{r Ecosystem categories in empirical data}
library(plyr)
df_new=df_emp
C=count(df_emp, 'Ecosystems')
print(C)
# remove categories <=3
remove=C[,2]<=3
remove_category=c()
for (i in 1:length(remove)){
  if(remove[i]==TRUE){
   df_new$Ecosystem[df_new$Ecosystem==C[i,1]]='others' 
  }
}

g1=ggplot(df_new, aes(x=Ecosystem, fill=Ecosystem)) + geom_bar()+ylab('Count')+theme(
  axis.text.x = element_text(size=14, angle=30),
  axis.title.x = element_text(size=24),
   axis.text.y = element_text(size=16),
  axis.title.y = element_text(size=24),
  legend.position="none"
  )
#ggsave("Cohen_Ecosystem_count.pdf")

# calclulate richness and FCLs in each ecosystem
g2=ggplot(data=df_new, aes(x=Ecosystem, y=Richness, color=Ecosystem)) +geom_jitter(position=position_jitter(0.2))+ylab('Richness')+theme(
axis.text.x = element_text(size=14, angle=30),
  axis.title.x = element_text(size=24),
   axis.text.y = element_text(size=16),
  axis.title.y = element_text(size=24),
  )+guides(color = 'none')
#ggsave("Cohen_Ecosystem_richness.pdf")


#ggplot(data=df_new, aes(x=Ecosystem, y=FCL_long, color=Ecosystem)) +geom_jitter(position=position_jitter(0.2))+ylab('FCL long')+theme(
g3=ggplot(df_new, aes(x=Ecosystem, y=FCL_long, color=Ecosystem)) + ylab('FCL long' )+
  geom_count(aes(size=..prop.., group=Ecosystem))+theme(
axis.text.x = element_text(size=14, angle=30),
  axis.title.x = element_text(size=24),
   axis.text.y = element_text(size=16),
  axis.title.y = element_text(size=24),
  )+guides(color = 'none')
#ggsave("Cohen_Ecosystem_long.pdf")

g4=ggplot(df_new, aes(x=Ecosystem, y=FCL_mean, color=Ecosystem)) + ylab('FCL mean')+
  geom_count(aes(size=..prop.., group=Ecosystem))+theme(
axis.text.x = element_text(size=14, angle=30),
  axis.title.x = element_text(size=24),
   axis.text.y = element_text(size=16),
  axis.title.y = element_text(size=24),
  #legend.position="none"
  )+guides(color = 'none')

#ggplot(data=df_new, aes(x=Ecosystem, y=FCL_short, color=Ecosystem)) +geom_jitter(position=position_jitter(0.2))+ylab('FCL short')+theme(
g5=ggplot(df_new, aes(x=Ecosystem, y=FCL_short, color=Ecosystem)) + ylab('FCL short')+
  geom_count(aes(size=..prop.., group=Ecosystem))+theme(
axis.text.x = element_text(size=14, angle=30),
  axis.title.x = element_text(size=24),
   axis.text.y = element_text(size=16),
  axis.title.y = element_text(size=24),
  #legend.position="none"
  )+guides(color = 'none')
#ggsave("Cohen_Ecosystem_short.pdf")
g1+g2+plot_spacer()+g3+g4+g5+plot_layout(nrow = 2, ncol=3)+plot_annotation(tag_levels = "A")&theme(plot.tag = element_text(size = 32))
ggsave('./empirical_pdf/Empirical_SI.pdf', heigh=12, width=16)
```
Next, we plot the cumulative probabilities over the two environmental factors
```{r resource and disturbance}
g1=ggplot(df_long, aes(richness, linetype=factor(resource), color=factor(disturbance)))+ stat_ecdf(geom = "step")
g1=g1+xlab('Richness')+ylab('Cumulative Prob.')  
g1=g1+xlim(c(0, 32))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position = 'none')+labs(linetype = "Resource", color='Disturbance')


g2=ggplot(df_mean, aes(richness, linetype=factor(resource), color=factor(disturbance)))+ stat_ecdf(geom = "step")
g2=g2+xlab('Richness')+ylab('Cumulative Prob.')  
g2=g2+xlim(c(0, 32))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position = 'none')+labs(linetype = "Resource", color='Disturbance')


g3=ggplot(df_short, aes(richness, linetype=factor(resource), color=factor(disturbance)))+ stat_ecdf(geom = "step")
g3=g3+xlab('Richness')+ylab('Cumulative Prob.')  
g3=g3+xlim(c(0, 32))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position = 'none')+labs(linetype = "Resource", color='Disturbance')

g4=ggplot(df_long, aes(chain, linetype=factor(resource), color=factor(disturbance)))+ stat_ecdf(geom = "step")
g4=g4+xlab('Chain')+ylab('Cumulative Prob.')  
g4=g4+xlim(c(0, 1))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20))+labs(linetype = "Resource", color='Disturbance')


g5=ggplot(df_mean, aes(chain, linetype=factor(resource), color=factor(disturbance)))+ stat_ecdf(geom = "step")
g5=g5+xlab('Chain')+ylab('Cumulative Prob.')  
g5=g5+xlim(c(0, 1))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20))+labs(linetype = "Resource", color='Disturbance')

g6=ggplot(df_short, aes(chain, linetype=factor(resource), color=factor(disturbance)))+ stat_ecdf(geom = "step")
g6=g6+xlab('Chain')+ylab('Cumulative Prob.')  
g6=g6+xlim(c(0, 1))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20))+labs(linetype = "Resource", color='Disturbance')

g1+g4+g2+g5+g3+g6+plot_layout(nrow = 3,)+plot_annotation(tag_levels = "A")&theme(plot.tag = element_text(size = 32))
ggsave('./Simulations/simulation_pdf/Cumulative_Richness_Chain_ver1.pdf', heigh=12, width=12)

```

```{r resource and ecosystem}
g1=ggplot(df_long, aes(richness, linetype=factor(resource), color=factor(ecosystem)))+ stat_ecdf(geom = "step")
g1=g1+xlab('Richness')+ylab('Cumulative Prob.')  
g1=g1+xlim(c(0, 32))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position = 'none')+labs(linetype = "Resource", color='Ecosystem')


g2=ggplot(df_mean, aes(richness, linetype=factor(resource), color=factor(ecosystem)))+ stat_ecdf(geom = "step")
g2=g2+xlab('Richness')+ylab('Cumulative Prob.')  
g2=g2+xlim(c(0, 32))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position = 'none')+labs(linetype = "Resource", color='Ecosystem')


g3=ggplot(df_short, aes(richness, linetype=factor(resource), color=factor(ecosystem)))+ stat_ecdf(geom = "step")
g3=g3+xlab('Richness')+ylab('Cumulative Prob.')  
g3=g3+xlim(c(0, 32))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position = 'none')+labs(linetype = "Resource", color='Ecosystem')

g4=ggplot(df_long, aes(chain, linetype=factor(resource), color=factor(ecosystem)))+ stat_ecdf(geom = "step")
g4=g4+xlab('Chain')+ylab('Cumulative Prob.')  
g4=g4+xlim(c(0, 1))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20))+labs(linetype = "Resource", color='Ecosystem')


g5=ggplot(df_mean, aes(chain, linetype=factor(resource), color=factor(ecosystem)))+ stat_ecdf(geom = "step")
g5=g5+xlab('Chain')+ylab('Cumulative Prob.')  
g5=g5+xlim(c(0, 1))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20))+labs(linetype = "Resource", color='Ecosystem')

g6=ggplot(df_short, aes(chain, linetype=factor(resource), color=factor(ecosystem)))+ stat_ecdf(geom = "step")
g6=g6+xlab('Chain')+ylab('Cumulative Prob.')  
g6=g6+xlim(c(0, 1))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20))+labs(linetype = "Resource", color='Ecosystem')

g1+g4+g2+g5+g3+g6+plot_layout(nrow = 3,)+plot_annotation(tag_levels = "A")&theme(plot.tag = element_text(size = 32))
ggsave('./Simulations/simulation_pdf/Cumulative_Richness_Chain_ver2.pdf', heigh=12, width=12)

```

```{r disturbance and ecosystem}
g1=ggplot(df_long, aes(richness, linetype=factor(disturbance), color=factor(ecosystem)))+ stat_ecdf(geom = "step")
g1=g1+xlab('Richness')+ylab('Cumulative Prob.')  
g1=g1+xlim(c(0, 32))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position = 'none')+labs(linetype = "Disturbance", color='Ecosystem')


g2=ggplot(df_mean, aes(richness, linetype=factor(disturbance), color=factor(ecosystem)))+ stat_ecdf(geom = "step")
g2=g2+xlab('Richness')+ylab('Cumulative Prob.')  
g2=g2+xlim(c(0, 32))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position = 'none')+labs(linetype = "Disturbance", color='Ecosystem')


g3=ggplot(df_short, aes(richness, linetype=factor(disturbance), color=factor(ecosystem)))+ stat_ecdf(geom = "step")
g3=g3+xlab('Richness')+ylab('Cumulative Prob.')  
g3=g3+xlim(c(0, 32))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position = 'none')+labs(linetype = "Disturbance", color='Ecosystem')

g4=ggplot(df_long, aes(chain, linetype=factor(disturbance), color=factor(ecosystem)))+ stat_ecdf(geom = "step")
g4=g4+xlab('Chain')+ylab('Cumulative Prob.')  
g4=g4+xlim(c(0, 1))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20))+labs(linetype = "Disturbance", color='Ecosystem')


g5=ggplot(df_mean, aes(chain, linetype=factor(disturbance), color=factor(ecosystem)))+ stat_ecdf(geom = "step")
g5=g5+xlab('Chain')+ylab('Cumulative Prob.')  
g5=g5+xlim(c(0, 1))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20))+labs(linetype = "Disturbance", color='Ecosystem')

g6=ggplot(df_short, aes(chain, linetype=factor(disturbance), color=factor(ecosystem)))+ stat_ecdf(geom = "step")
g6=g6+xlab('Chain')+ylab('Cumulative Prob.')  
g6=g6+xlim(c(0, 1))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20))+labs(linetype = "Disturbance", color='Ecosystem')

g1+g4+g2+g5+g3+g6+plot_layout(nrow = 3,)+plot_annotation(tag_levels = "A")&theme(plot.tag = element_text(size = 32))
ggsave('./Simulations/simulation_pdf/Cumulative_Richness_Chain_ver3.pdf', heigh=12, width=12)

```


```{r correlation heat map}
library(tidyverse)
library(igraph)
library(Matrix)
library(ggplot2)
library(patchwork)
library(ggcorrplot)

df_emp=read.csv("Cohen2010_summary.csv") # empirical data
df_long=read.csv("./FCL_long_simulations_summary.csv") # simulation using FCL long
df_mean=read.csv("./FCL_mean_simulations_summary.csv") # simulation using FCL mean
df_short=read.csv("./FCL_short_simulations_summary.csv") # simulation using FCL short

# Preparing data analysis
# For df_emp, we removed unnecessary columns and convert the count data of motives into fractions
df_emp = subset(df_emp, select = -c(empty,monoA.single, bi.single) )
df_emp=df_emp %>% select(order(colnames(df_emp)))
df_emp=dplyr::select(df_emp, WEB_id,Ecosystem, FCL_long,FCL_mean, FCL_short,richness,Ecosystem, everything())
sum.motif=apply(df_emp[, 7:ncol(df_emp)], 1, sum) # sum of motives in each row
df_emp[, 7:ncol(df_emp)] = df_emp[, 7:ncol(df_emp)]/sum.motif # converting into fractions of motives
# we remove motives that do not  or rarely appear
df_emp = subset(df_emp, select = -c(WEB_id, d1, d2,d3, d4, s3, d5, d6, d7,d8) )
colnames(df_emp) = c('Ecosystems', 'FCL_long', 'FCL_mean', 'FCL_short', 'Richness', 
                     'Chain', 'Omnivory', 'Apparent', 'Exploitative')

df_long=df_long[, c(2:4,6:ncol(df_long))]
colnames(df_long)=c('Resource', 'Disturbance',  'Ecosystem',  'FCL',
                    'Chain',  'Omnivory',  'Apparent', 'Exploitative',  'Richness')
df_long=df_long[, c('Resource', 'Disturbance',  'Ecosystem',  'FCL','Richness',
                    'Chain',  'Omnivory',  'Apparent', 'Exploitative' )]
df_mean=df_mean[, c(2:4, 6:ncol(df_mean))]
colnames(df_mean)=c('Resource', 'Disturbance',  'Ecosystem',  'FCL','Richness',
                    'Chain',  'Omnivory',  'Apparent', 'Exploitative' )
df_short=df_short[, c(2:4, 6:ncol(df_short))]
colnames(df_short)=c('Resource', 'Disturbance',  'Ecosystem',  'FCL','Richness',
                    'Chain', 'Omnivory',  'Apparent', 'Exploitative' )

corr1=cor(df_emp[, 2:ncol(df_emp)], use = "pairwise.complete.obs", method='spearman') # pearson and spearman show similar results
g1=ggcorrplot(corr1, type = "lower", lab = TRUE)

corr2=cor(df_long, use = "pairwise.complete.obs", method='spearman') # pearson and spearman show similar results
g2=ggcorrplot(corr2, type = "lower", lab = TRUE)

corr3=cor(df_mean, use = "pairwise.complete.obs", method='spearman') # pearson and spearman show similar results
g3=ggcorrplot(corr3, type = "lower", lab = TRUE)

corr4=cor(df_short, use = "pairwise.complete.obs", method='spearman') # pearson and spearman show similar results
g4=ggcorrplot(corr4, type = "lower", lab = TRUE)

g=g1+g2+g3+g4+plot_layout(nrow = 2)+plot_annotation(tag_levels = "A")&theme(plot.tag = element_text(size = 32))
ggsave('./HeatMapCorrelation.pdf', heigh=12, width=12)


```