---
title: "Plot and analysis"
output: html_notebook
---

In this notebook, we analyze whether species richness and chain motives modulate the relationship between FCL and three enviornmental factors (resource availability, disturbances, and ecosystem sizes).
First, we investigate whether species richness and food web motives correlate with FCL or not.

```{r Read csv data}
library(ggplot2)
library(patchwork)
library(tidyverse)

df_emp=read.csv("Cohen2010_summary.csv") # empirical data
df_long=read.csv("./Simulations/FCL_long_simulations_summary.csv") # simulation using FCL long
df_mean=read.csv("./Simulations/FCL_mean_simulations_summary.csv") # simulation using FCL mean
df_short=read.csv("./Simulations/FCL_short_simulations_summary.csv") # simulation using FCL short

# Preparing data analysis
# For df_emp, we removed unnecessary columns and convert the count data of motives into fractions
df_emp = subset(df_emp, select = -c(empty,monoA.single, bi.single) )
df_emp=df_emp %>% select(order(colnames(df_emp)))
df_emp=dplyr::select(df_emp, WEB_id,Ecosystem, FCL_long,FCL_short,richness,Ecosystem, everything())
sum.motif=apply(df_emp[, 6:ncol(df_emp)], 1, sum) # sum of motives in each row
df_emp[, 6:ncol(df_emp)] = df_emp[, 6:ncol(df_emp)]/sum.motif # converting into fractions of motives
# we remove motives that do not  or rarely appear
df_emp = subset(df_emp, select = -c(WEB_id, d1, d2,d3, d4, s3, d5, d6, d7,d8) )
colnames(df_emp) = c('Ecosystems', 'FCL_long', 'FCL_short', 'Richness', 
                 'Chain', 'Omnivory', 'Apparent', 'Exploitative')
```
Next we plot FCL against the richness and motives 

```{r Empirical richness and motives}
r1=ggplot(df_emp, aes(x=Richness, y=FCL_long, size=4, alpha=0.5))+geom_point(color='black')+ylab('FCL long')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+annotate(geom="text", x=40, y=9, label=paste0('corr.=', round(cor.test(na.omit(df_emp)$FCL_long, na.omit(df_emp)$Richness, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(na.omit(df_emp)$FCL_long, na.omit(df_emp)$Richness, method='spearman')$p.value, 3)), size=5)
# Note df_emp$FCL_long includes some NA because of cyclic food webs
r2=ggplot(df_emp, aes(x=Richness, y=FCL_short, size=4, alpha=0.5))+geom_point(color='black')+ylab('FCL short')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+annotate(geom="text", x=40, y=3.75, label=paste0('corr.=', round(cor.test(df_emp$FCL_short, df_emp$Richness, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df_emp$FCL_short, df_emp$Richness, method='spearman')$p.value, 3)), size=5)

m1=ggplot(df_emp, aes(x=Chain, y=FCL_long, size=4, alpha=0.5))+geom_point(color='#a6cee3')+ylab('FCL long')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=9, label=paste0('corr.=', round(cor.test(df_emp$FCL_long, df_emp$Chain, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df_emp$FCL_long, df_emp$Chain, method='spearman')$p.value, 3)), size=5)

m2=ggplot(df_emp, aes(x=Omnivory, y=FCL_long, size=4, alpha=0.5))+geom_point(color='#1f78b4')+ylab('FCL long')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )  +xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=9, label=paste0('corr.=', round(cor.test(df_emp$FCL_long, df_emp$Omnivory, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df_emp$FCL_long, df_emp$Omnivory, method='spearman')$p.value, 3)), size=5)

m3=ggplot(df_emp, aes(x=Apparent, y=FCL_long, size=4, alpha=0.5))+geom_point(color='#b2df8a')+ylab('FCL long')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=9, label=paste0('corr.=', round(cor.test(df_emp$FCL_long, df_emp$Apparent, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df_emp$FCL_long, df_emp$Apparent, method='spearman')$p.value, 3)), size=5)

m4=ggplot(df_emp, aes(x=Exploitative, y=FCL_long, size=4, alpha=0.5))+geom_point(color='#33a02c')+ylab('FCL long')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=9, label=paste0('corr.=', round(cor.test(df_emp$FCL_long, df_emp$Exploitative, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df_emp$FCL_long, df_emp$Exploitative, method='spearman')$p.value, 3)), size=5)


m5=ggplot(df_emp, aes(x=Chain, y=FCL_short, size=4, alpha=0.5))+geom_point(color='#a6cee3')+ylab('FCL short')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=3.75, label=paste0('corr.=', round(cor.test(df_emp$FCL_short, df_emp$Chain, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df_emp$FCL_short, df_emp$Chain, method='spearman')$p.value, 3)), size=5)

m6=ggplot(df_emp, aes(x=Omnivory, y=FCL_short, size=4, alpha=0.5))+geom_point(color='#1f78b4')+ylab('FCL short')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )  +xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=3.75, label=paste0('corr.=', round(cor.test(df_emp$FCL_short, df_emp$Omnivory, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df_emp$FCL_short, df_emp$Omnivory, method='spearman')$p.value, 3)), size=5)

m7=ggplot(df_emp, aes(x=Apparent, y=FCL_short, size=4, alpha=0.5))+geom_point(color='#b2df8a')+ylab('FCL short')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=3.75, label=paste0('corr.=', round(cor.test(df_emp$FCL_short, df_emp$Apparent, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df_emp$FCL_short, df_emp$Apparent, method='spearman')$p.value, 3)), size=5)

m8=ggplot(df_emp, aes(x=Exploitative, y=FCL_short, size=4, alpha=0.5))+geom_point(color='#33a02c')+ylab('FCL short')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=3.75, label=paste0('corr.=', round(cor.test(df_emp$FCL_short, df_emp$Exploitative, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df_emp$FCL_short, df_emp$Exploitative, method='spearman')$p.value, 3)), size=5)

g=r1+r2+m1+m5+m2+m6+m3+m7+m4+m8+plot_layout(nrow = 5, ncol=2)+plot_annotation(tag_levels = "A")&theme(plot.tag = element_text(size = 32))

ggsave('./empirical_pdf/FCL_empirical.pdf', width=8, height=12)
```

```{r Simulated richness and motives}
# Note: if richness =0 or 1 => motives cannot be defined and correponding data are removed 
r1=ggplot(df_long, aes(x=richness, y=FCL, size=3, alpha=0.005))+geom_point(color='black')+ylab('FCL long')+xlab("Richness")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+annotate(geom="text", x=10, y=11, label=paste0('corr.=', round(cor.test(df_long$FCL, df_long$richness, method='spearman')$estimate, 3)), size=5)
r2=ggplot(df_mean, aes(x=richness, y=FCL, size=3, alpha=0.005))+geom_point(color='black')+ylab('FCL mean')+xlab("Richness")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+annotate(geom="text", x=10, y=9, label=paste0('corr.=', round(cor.test(df_mean$FCL, df_mean$richness, method='spearman')$estimate, 3)), size=5)
r3=ggplot(df_short, aes(x=richness, y=FCL, size=3, alpha=0.005))+geom_point(color='black')+ylab('FCL short')+xlab("Richness")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+annotate(geom="text", x=10, y=9, label=paste0('corr.=', round(cor.test(df_short$FCL, df_short$richness, method='spearman')$estimate, 3)), size=5)

m1=ggplot(df_long, aes(x=chain, y=FCL, size=4, alpha=0.1))+geom_point(color='#a6cee3')+ylab('FCL long')+xlab("Chain")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=11, label=paste0('corr.=', round(cor.test(df_long$FCL, df_long$chain, method='spearman')$estimate, 3)), size=5)

m2=ggplot(df_long, aes(x=omnivory, y=FCL, size=4, alpha=0.1))+geom_point(color='#1f78b4')+ylab('FCL long')+xlab("Omnivory")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=11, label=paste0('corr.=', round(cor.test(df_long$FCL, df_long$omnivory, method='spearman')$estimate, 3)), size=5)

m3=ggplot(df_long, aes(x=apparent, y=FCL, size=4, alpha=0.1))+geom_point(color='#b2df8a')+ylab('FCL long')+xlab("Apparent")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=11, label=paste0('corr.=', round(cor.test(df_long$FCL, df_long$apparent, method='spearman')$estimate, 3)), size=5)

m4=ggplot(df_long, aes(x=exploitative, y=FCL, size=4, alpha=0.1))+geom_point(color='#33a02c')+ylab('FCL long')+xlab("Exploitative")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=11, label=paste0('corr.=', round(cor.test(df_long$FCL, df_long$exploitative, method='spearman')$estimate, 3)), size=5)


m5=ggplot(df_mean, aes(x=chain, y=FCL, size=4, alpha=0.1))+geom_point(color='#a6cee3')+ylab('FCL mean')+xlab("Chain")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=9, label=paste0('corr.=', round(cor.test(df_mean$FCL, df_mean$chain, method='spearman')$estimate, 3)), size=5)

m6=ggplot(df_mean, aes(x=omnivory, y=FCL, size=4, alpha=0.1))+geom_point(color='#1f78b4')+ylab('FCL mean')+xlab("Omnivory")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=9, label=paste0('corr.=', round(cor.test(df_mean$FCL, df_mean$omnivory, method='spearman')$estimate, 3)), size=5)

m7=ggplot(df_mean, aes(x=apparent, y=FCL, size=4, alpha=0.1))+geom_point(color='#b2df8a')+ylab('FCL mean')+xlab("Apparent")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=9, label=paste0('corr.=', round(cor.test(df_mean$FCL, df_mean$apparent, method='spearman')$estimate, 3)), size=5)

m8=ggplot(df_mean, aes(x=exploitative, y=FCL, size=4, alpha=0.1))+geom_point(color='#33a02c')+ylab('FCL mean')+xlab("Exploitative")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=9, label=paste0('corr.=', round(cor.test(df_mean$FCL, df_mean$exploitative, method='spearman')$estimate, 3)), size=5)

m9=ggplot(df_short, aes(x=chain, y=FCL, size=4, alpha=0.1))+geom_point(color='#a6cee3')+ylab('FCL short')+xlab("Chain")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=9, label=paste0('corr.=', round(cor.test(df_short$FCL, df_short$chain, method='spearman')$estimate, 3)), size=5)

m10=ggplot(df_short, aes(x=omnivory, y=FCL, size=4, alpha=0.1))+geom_point(color='#1f78b4')+ylab('FCL short')+xlab("Omnivory")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=9, label=paste0('corr.=', round(cor.test(df_short$FCL, df_short$omnivory, method='spearman')$estimate, 3)), size=5)

m11=ggplot(df_short, aes(x=apparent, y=FCL, size=4, alpha=0.1))+geom_point(color='#b2df8a')+ylab('FCL short')+xlab("Apparent")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=9, label=paste0('corr.=', round(cor.test(df_short$FCL, df_short$apparent, method='spearman')$estimate, 3)), size=5)

m12=ggplot(df_short, aes(x=exploitative, y=FCL, size=4, alpha=0.1))+geom_point(color='#33a02c')+ylab('FCL short')+xlab("Exploitative")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=9, label=paste0('corr.=', round(cor.test(df_short$FCL, df_short$exploitative, method='spearman')$estimate, 3)), size=5)

r1+r2+r3+m1+m5+m9+m2+m6+m10+m3+m7+m11+m4+m8+m12+plot_layout(nrow = 5, ncol=3)+plot_annotation(tag_levels = "A")&theme(plot.tag = element_text(size = 32))
ggsave('./Simulations/simulation_pdf/FCL_simulation_correlation.png', width=12, height=16)

```

Next, we analyze how species richness and food web motives affect FCL.
We assume three functional responses: linear, saturating, or quadratic.
We calculate the Akaike Information criterion of 15 models given FCL 
in empirical data set or simulation data.

```{r Model selection in empirical data}
b_start=0.5 # need to tune initial guess so that the algortihm works
AIC_cal2= function(df){
  #-------------Model description------------------------
  model1=nls(formula = FCL + 1 ~ a*Richness, data = df, algorithm='port', 
             lower=c(a=0), upper=c(a=max(df$FCL)+1), start=c(a=1))
  model2=nls(FCL ~ a*(1-exp(-b*Richness))-1, data=df, start=c(a=max(df$FCL)/2, b=b_start),  
             algorithm='port', lower=c(a=0, b=0), upper=c(a=max(df$FCL)+1, b =10)) # saturating func of richness
  model3=nls(FCL ~ -a*Richness^2+b*Richness-1, data=df, start=c(a=1, b=1), 
             algorithm='port', lower=c(a=0, b=0), upper=c(a=10, b=10)) # quadratic func of richness
  model4=nls(formula = FCL + 1 ~ a*Chain, data = df,
             algorithm='port', lower=c(a=0), upper=c(a=max(df$FCL)+1), start=c(a=1))# linear func of chain
  model5=nls(FCL ~ a*(1-exp(-b*Chain))-1, data=df, start=c(a=max(df$FCL)/2, b=b_start),  
             algorithm='port', lower=c(a=0, b=0), upper=c(a=max(df$FCL)+1, b=10)) # saturating func of chain
  model6=nls(FCL ~ -a*Chain^2+b*Chain-1, data=df, start=c(a=1, b=1), 
             algorithm='port', lower=c(a=0, b=0), upper=c(a=10, b=10)) # quadratic func of chain
 
  #combination of chain and richness
  model14=glm(formula = FCL + 1 ~ Richness*Chain, family = poisson(link = "log"), 
    data = df)# linear func of chain
  model15=nls(FCL ~ a*Richness+b*(1-exp(-c*Chain))-1, data=df, start=c(a=0.1, b=max(df$FCL)/2, c=b_start), 
              algorithm='port', lower=c(a=0, b=0, c=0), upper=c(a=10, b=max(df$FCL)+1, c=10))
  model16=nls(FCL ~ a*Richness-b*Chain^2+c*Chain-1, data=df, start=c(a=0.1, b=1, c=1), 
              algorithm='port', lower=c(a=0, b=0, c=0), upper=c(a=10, b=10, c=10))
  model24=nls(FCL ~ a*(1-exp(-b*Richness))+c*Chain-1, data=df, start=c(a=max(df$FCL)/2, b=b_start, c=1),
              algorithm='port', lower=c(a=0, b=0, c=0), upper=c(a=max(df$FCL)+1, b=10, c=10))
  model25=nls(FCL ~ a*(1-exp(-b*Richness))+c*(1-exp(-d*Chain))-1, data=df, 
              start=c(a=max(df$FCL)/2, b=b_start, c=max(df$FCL)/2, d=b_start), 
              algorithm='port', lower=c(a=0, b=0, c=0, d=0),
              upper=c(a=max(df$FCL)+1, b=10, c=max(df$FCL)+1, d=10))
  model26=nls(FCL ~ a*(1-exp(-b*Richness))-c*Chain^2+d*Chain-1, data=df, 
              start=c(a=max(df$FCL)/2, b=b_start, c=1, d=1.05), # d= 1 cause a problem of conversence
              algorithm='port', lower=c(a=0, b=0, c=0, d=0), 
              upper=c(a=max(df$FCL)+1, b=10, c=10, d=10))
  model34=nls(FCL ~ -a*Richness^2+b*Richness+c*Chain-1, data=df, start=c(a=1, b=1, c=1),
              algorithm='port', lower=c(a=0, b=0, c=0),
              upper=c(a=10, b=10, c=10))
  model35=nls(FCL ~ -a*Richness^2+b*Richness+c*(1-exp(-d*Chain))-1, data=df, 
              start=c(a=1, b=1, c=max(df$FCL)/2, d=b_start), 
              algorithm='port', lower=c(a=0, b=0, c=0, d=0), 
              upper=c(a=10, b=10, c=max(df$FCL)+1, d=10))
  model36=nls(FCL ~ -a*Richness^2+b*Richness-c*Chain^2+d*Chain-1, data=df, 
              start=c(a=1, b=1, c=1, d=1),
              algorithm='port', lower=c(a=0, b =0, c=0, d=0), 
              upper=c(a=10, b=10, c=10, d=10))
  
  AICs=c(AIC(model1), AIC(model2), AIC(model3), AIC(model4), AIC(model5), AIC(model6),
         AIC(model14),AIC(model15), AIC(model16), AIC(model24), AIC(model25), AIC(model26),
         AIC(model34),AIC(model35), AIC(model36))
  minAIC=min(AICs)
  deltaAIC=AICs-minAIC
  print(AICs)
  
  print(minAIC)
  
  print(deltaAIC)
  
  #print(summary(models[which.max(deltaAIC)]))
}

df_emp$FCL=df_emp$FCL_long
#FCL long
AIC_cal2(na.omit(df_emp)) # we omit FCL na in cyclic food webs
#FCL short
df_emp$FCL=df_emp$FCL_short
AIC_cal2(df_emp)
```
The best models are saturating + quadriatic (in FCL long) or saturating + linear (in FCL short). However, in the FCL short, using saturating or quadratic functions in chain also seem fine. 
Below, we show the coefficnet values in the best models and plot them.

```{r Best models in mepirical data}
# FCL_long
summary(nls(FCL_long ~ a*(1-exp(-b*Richness))-c*Chain^2+d*Chain-1, data=na.omit(df_emp), 
              start=c(a=max(na.omit(df_emp)$FCL_long)/2, b=b_start, c=1, d=1.05), # d= 1 cause a problem of conversence
              algorithm='port', lower=c(a=0, b=0, c=0, d=0), 
              upper=c(a=max(na.omit(df_emp)$FCL_long)+1, b=10, c=10, d=10)))
# FCL short
summary(nls(FCL_short ~ a*(1-exp(-b*Richness))+c*Chain-1, data=df_emp, start=c(a=max(df_emp$FCL_short)/2, b=b_start, c=1),
              algorithm='port', lower=c(a=0, b=0, c=0), upper=c(a=max(df_emp$FCL_short)+1, b=10, c=10)))
```
```{r Plotting best models with empirical data}
df_emp$predict_short=2.85*(1-exp(-0.19*df_emp$Richness))+2.12*df_emp$Chain-1


g1=ggplot(df_emp, aes(x=Richness, y=FCL_short, size=3, alpha=0.000005))+geom_point(color='black')+ylab('FCL short')+xlab("Richness")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun = function(x) 2.85*(1-exp(-0.19*x))+2.12*mean(df_emp$Chain)-1, color='red')
g2=ggplot(df_emp, aes(x=Chain, y=FCL_short, size=3, alpha=0.000005))+geom_point(color='black')+ylab('FCL short')+xlab("Chain")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun = function(x) 2.85*(1-exp(-0.19*mean(df_emp$Richness)))+2.12*x-1, color='red')

g3=ggplot(df_emp, aes(x=FCL_short, y=predict_short, size=3, alpha=0.000005))+geom_point(color='black')+ylim(c(-1, 6))+xlab('FCL short')+ylab("Model prediction")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun=function(x) x, color='blue')

df_emp$predict_long=3.94*(1-exp(-0.09*df_emp$Richness))-7.3*df_emp$Chain^2+9.45*df_emp$Chain-1

g4=ggplot(df_emp, aes(x=Richness, y=FCL_long, size=3, alpha=0.000005))+geom_point(color='black')+ylab('FCL long')+xlab("Richness")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun = function(x) 3.94*(1-exp(-0.09*x))-7.3*mean(df_emp$Chain)^2+9.45*mean(df_emp$Chain)-1, color='red')
g5=ggplot(df_emp, aes(x=Chain, y=FCL_long, size=3, alpha=0.000005))+geom_point(color='black')+ylab('FCL long')+xlab("Chain")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun = function(x) 3.94*(1-exp(-0.09*mean(df_emp$Richness)))-7.3*x^2+9.45*x-1, color='red')
g6=ggplot(df_emp, aes(x=FCL_long, y=predict_long, size=3, alpha=0.000005))+geom_point(color='black')+ylim(c(-1, 6))+xlab('FCL long')+ylab("Model prediction")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun=function(x) x, color='blue')
g4+g5+g6+g1+g2+g3+plot_layout(nrow = 2)+plot_annotation(tag_levels = "A")&theme(plot.tag = element_text(size = 32))
ggsave('./empirical_pdf/Modeling_empirical.png', width=12, height=8)
```

```{r best models in simulaiton}
b_start=1.5 # need to tune initial guess so that the algortihm works
AIC_cal1= function(df, b_start=1.5){
    model1=nls(FCL ~ a*richness-1, data=df, start=c(a=1), algorithm='port', 
             lower=c(a=0), upper=c(a=10)) # linear func of richness
  model2=nls(FCL ~ a*(1-exp(-b*richness))-1, data=df, start=c(a=max(df$FCL)/2, b=b_start),  
             algorithm='port', lower=c(a=0, b=0), upper=c(a=max(df$FCL)+1, b =10)) # saturating func of richness
  model3=nls(FCL ~ -a*richness^2+b*richness-1, data=df, start=c(a=1, b=1), 
             algorithm='port', lower=c(a=0, b=0), upper=c(a=10, b=10)) # quadratic func of richness
  model4=nls(FCL ~ a*chain-1, data=df, start=c(a=1),  
             algorithm='port',lower=c(a=0), upper=(a=10)) # linear func of chain
  model5=nls(FCL ~ a*(1-exp(-b*chain))-1, data=df, start=c(a=max(df$FCL)/2, b=b_start),  
             algorithm='port', lower=c(a=0, b=0), upper=c(a=max(df$FCL)+1, b=10)) # saturating func of chain
  model6=nls(FCL ~ -a*chain^2+b*chain-1, data=df, start=c(a=1, b=1), 
             algorithm='port', lower=c(a=0, b=0), upper=c(a=10, b=10)) # quadratic func of chain
 
  #combination of chain and richness
  model14=nls(FCL ~ a*richness+b*chain-1, data=df, start=c(a=1, b=1), algorithm='port', 
              lower = c(a=0, b=0), upper=c(a=10, b=10))
  model15=nls(FCL ~ a*richness+b*(1-exp(-c*chain))-1, data=df, start=c(a=1, b=max(df$FCL)/2, c=b_start), 
              algorithm='port', lower=c(a=0, b=0, c=0), upper=c(a=10, b=max(df$FCL)+1, c=10))
  model16=nls(FCL ~ a*richness-b*chain^2+c*chain-1, data=df, start=c(a=1, b=1, c=1), 
              algorithm='port', lower=c(a=0, b=0, c=0), upper=c(a=10, b=10, c=10))
  model24=nls(FCL ~ a*(1-exp(-b*richness))+c*chain-1, data=df, start=c(a=max(df$FCL)/2, b=b_start, c=1),
              algorithm='port', lower=c(a=0, b=0, c=0), upper=c(a=max(df$FCL)+1, b=10, c=10), 
              control= nls.control(maxiter = 500))
  model25=nls(FCL ~ a*(1-exp(-b*richness))+c*(1-exp(-d*chain))-1, data=df, 
              start=c(a=max(df$FCL)/2, b=2*b_start, c=max(df$FCL)/2, d=2*b_start), 
              algorithm='port', lower=c(a=0, b=0, c=0, d=0),
              upper=c(a=max(df$FCL)+1, b=10, c=max(df$FCL)+1, d=10))
  model26=nls(FCL ~ a*(1-exp(-b*richness))-c*chain^2+d*chain-1, data=df, 
              start=c(a=max(df$FCL)/2, b=b_start, c=1, d=1), 
              algorithm='port', lower=c(a=0, b=0, c=0, d=0), 
              upper=c(a=max(df$FCL)+1, b=10, c=10, d=10))
  model34=nls(FCL ~ -a*richness^2+b*richness+c*chain-1, data=df, start=c(a=1, b=1, c=1),
              algorithm='port', lower=c(a=0, b=0, c=0),
              upper=c(a=10, b=10, c=10))
  model35=nls(FCL ~ -a*richness^2+b*richness+c*(1-exp(-d*chain))-1, data=df, 
              start=c(a=1, b=1, c=max(df$FCL)/2, d=b_start), 
              algorithm='port', lower=c(a=0, b=0, c=0, d=0), 
              upper=c(a=10, b=10, c=max(df$FCL)+1, d=10))
  model36=nls(FCL ~ -a*richness^2+b*richness-c*chain^2+d*chain-1, data=df, 
              start=c(a=1, b=1, c=1, d=1),
              algorithm='port', lower=c(a=0, b =0, c=0, d=0), 
              upper=c(a=10, b=10, c=10, d=10))
  
  AICs=c(AIC(model1), AIC(model2), AIC(model3), AIC(model4), AIC(model5), AIC(model6),
         AIC(model14),AIC(model15), AIC(model16), AIC(model24), AIC(model25), AIC(model26),
         AIC(model34),AIC(model35), AIC(model36))
   minAIC=min(AICs)
  deltaAIC=AICs-minAIC
  print(deltaAIC)
  print(minAIC)
}

#FCL long
AIC_cal1(df_long) 
#FCL mean
AIC_cal1(df_mean)
#FCL short
AIC_cal1(df_short, 2) # to avoid bad convergence

```

```{r the best models in simulation data}
model_long=nls(FCL ~ a*(1-exp(-b*richness))-c*chain^2+d*chain-1, data=df_long, 
              start=c(a=max(df_long$FCL)/2, b=b_start, c=1, d=1), 
              algorithm='port', lower=c(a=0, b=0, c=0, d=0), 
              upper=c(a=max(df_long$FCL)+1, b=10, c=10, d=10))
summary(model_long)

model_mean=nls(FCL ~ a*(1-exp(-b*richness))-c*chain^2+d*chain-1, data=df_mean, 
              start=c(a=max(df_mean$FCL)/2, b=b_start, c=1, d=1), 
              algorithm='port', lower=c(a=0, b=0, c=0, d=0), 
              upper=c(a=max(df_mean$FCL)+1, b=10, c=10, d=10))
summary(model_mean)

model_short=nls(FCL ~ a*(1-exp(-b*richness))-c*chain^2+d*chain-1, data=df_short, 
              start=c(a=max(df_short$FCL)/2, b=2, c=1, d=1), 
              algorithm='port', lower=c(a=0, b=0, c=0, d=0), 
              upper=c(a=max(df_short$FCL)+1, b=10, c=10, d=10))
summary(model_short)

```

```{r best models for simulation data}
# First we fill na with 0s (corresponding richness < 2)

df_long$predict=6.92*(1-exp(-0.08*df_long$richness))-1.49*replace(df_long,is.na(df_long),0)$chain^2+3.15*replace(df_long,is.na(df_long),0)$chain-1 # replace na with 0
g1=ggplot(df_long, aes(x=richness, y=FCL, size=3, alpha=0.000005))+geom_point(color='black')+ylab('FCL long')+xlab("Richness")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun = function(x) 6.92*(1-exp(-0.08*x))-1.49*mean(df_long$chain, na.rm=TRUE)^2+3.15*mean(df_long$chain, na.rm=TRUE)-1, color='red')
g2=ggplot(df_long, aes(x=chain, y=FCL, size=3, alpha=0.000005))+geom_point(color='black')+ylab('FCL long')+xlab("Chain")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun = function(x) 6.92*(1-exp(-0.08*mean(df_long$richness)))-1.49*x^2+3.15*x-1, color='red')
g3=ggplot(df_long, aes(x=FCL, y=predict, size=3, alpha=0.000005))+geom_point(color='black')+ylim(c(-1, 6))+xlab('FCL long')+ylab("Model prediction")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun=function(x) x, color='blue')

# FCL mean 
df_mean$predict=3.81*(1-exp(-0.17*df_mean$richness))-0.91*replace(df_mean,is.na(df_mean),0)$chain^2+2.43*replace(df_mean,is.na(df_mean),0)$chain-1
g4=ggplot(df_mean, aes(x=richness, y=FCL, size=3, alpha=0.000005))+geom_point(color='black')+ylab('FCL mean')+xlab("Richness")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun = function(x) 3.81*(1-exp(-0.17*x))-0.91*mean(df_mean$chain, na.rm=TRUE)^2+2.43*mean(df_mean$chain, na.rm=TRUE)-1, color='red')
g5=ggplot(df_mean, aes(x=chain, y=FCL, size=3, alpha=0.000005))+geom_point(color='black')+ylab('FCL mean')+xlab("Chain")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun = function(x) 3.81*(1-exp(-0.17*mean(df_mean$richness)))-0.91*x^2+2.43*x-1, color='red')
g6=ggplot(df_mean, aes(x=FCL, y=predict, size=3, alpha=0.000005))+geom_point(color='black')+ylim(c(-1, 6))+xlab('FCL mean')+ylab("Model prediction")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun=function(x) x, color='blue')

#FCL short
df_short$predict=2.98*(1-exp(-0.24*df_short$richness))-0.69*replace(df_short,is.na(df_short),0)$chain^2+2.13*replace(df_short,is.na(df_short),0)$chain-1
g7=ggplot(df_short, aes(x=richness, y=FCL, size=3, alpha=0.000005))+geom_point(color='black')+ylab('FCL short')+xlab("Richness")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun = function(x) 2.98*(1-exp(-0.24*x))-0.69*mean(df_short$chain, na.rm=TRUE)^2+2.13*mean(df_short$chain, na.rm=TRUE)-1, color='red')
g8=ggplot(df_short, aes(x=chain, y=FCL, size=3, alpha=0.000005))+geom_point(color='black')+ylab('FCL short')+xlab("Chain")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun = function(x) 2.98*(1-exp(-0.24*mean(df_short$richness)))-0.69*x^2+2.13*x-1, color='red')
g9=ggplot(df_short, aes(x=FCL, y=predict, size=3, alpha=0.000005))+geom_point(color='black')+ylim(c(-1, 6))+xlab('FCL short')+ylab("Model prediction")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+stat_function(fun=function(x) x, color='blue')

g1+g2+g3+g4+g5+g6+g7+g8+g9+plot_layout(nrow = 3,)+plot_annotation(tag_levels = "A")&theme(plot.tag = element_text(size = 32))

ggsave('./Simulations/simulation_pdf/Modeling_simulations.png', width=12, height=8)

```

Now we show how the three environmental drivers relate to FCL, species richness and the chain motif.
First, we check the relationships between enviornments and FCL

```{r Eviornment vs FCL}
p1=ggplot(df_long, aes(x=factor(resource), y=FCL))+geom_violin(color='#7570b3')+ylab('FCL long')+xlab("Resource")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+annotate(geom="text", x=2, y=11, label=paste0('corr.=', round(cor.test(df_long$FCL, df_long$resource, method='spearman')$estimate, 3)), size=5)

p2=ggplot(df_long, aes(x=factor(disturbance), y=FCL))+geom_violin(color='#d95f02')+ylab('FCL long')+xlab("Disturbance")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+annotate(geom="text", x=1.5, y=11, label=paste0('corr.=', round(cor.test(df_long$FCL, df_long$disturbance, method='spearman')$estimate, 3)), size=5)

p3=ggplot(df_long, aes(x=factor(ecosystem), y=FCL))+geom_violin(color='#1b9e77')+ylab('FCL long')+xlab("Ecosystem")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+annotate(geom="text", x=1.5, y=11, label=paste0('corr.=', round(cor.test(df_long$FCL, df_long$ecosystem, method='spearman')$estimate, 3)), size=5)


p4=ggplot(df_mean, aes(x=factor(resource), y=FCL))+geom_violin(color='#7570b3')+ylab('FCL mean')+xlab("Resource")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+annotate(geom="text", x=2, y=9, label=paste0('corr.=', round(cor.test(df_mean$FCL, df_mean$resource, method='spearman')$estimate, 3)), size=5)

p5=ggplot(df_mean, aes(x=factor(disturbance), y=FCL))+geom_violin(color='#d95f02')+ylab('FCL mean')+xlab("Disturbance")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+annotate(geom="text", x=1.5, y=9, label=paste0('corr.=', round(cor.test(df_mean$FCL, df_mean$disturbance, method='spearman')$estimate, 3)), size=5)

p6=ggplot(df_mean, aes(x=factor(ecosystem), y=FCL))+geom_violin(color='#1b9e77')+ylab('FCL mean')+xlab("Ecosystem")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+annotate(geom="text", x=1.5, y=9, label=paste0('corr.=', round(cor.test(df_mean$FCL, df_mean$ecosystem, method='spearman')$estimate, 3)), size=5)


p7=ggplot(df_short, aes(x=factor(resource), y=FCL))+geom_violin(color='#7570b3')+ylab('FCL short')+xlab("Resource")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+annotate(geom="text", x=2, y=9, label=paste0('corr.=', round(cor.test(df_short$FCL, df_short$resource, method='spearman')$estimate, 3)), size=5)

p8=ggplot(df_short, aes(x=factor(disturbance), y=FCL))+geom_violin(color='#d95f02')+ylab('FCL short')+xlab("Disturbance")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+annotate(geom="text", x=1.5, y=9, label=paste0('corr.=', round(cor.test(df_short$FCL, df_short$disturbance, method='spearman')$estimate, 3)), size=5)

p9=ggplot(df_short, aes(x=factor(ecosystem), y=FCL))+geom_violin(color='#1b9e77')+ylab('FCL short')+xlab("Ecosystem")+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+annotate(geom="text", x=1.5, y=9, label=paste0('corr.=', round(cor.test(df_short$FCL, df_short$ecosystem, method='spearman')$estimate, 3)), size=5)

p1+p4+p7+p2+p5+p8+p3+p6+p9+plot_layout(nrow = 3,)+plot_annotation(tag_levels = "A")&theme(plot.tag = element_text(size = 32))
ggsave('./Simulations/simulation_pdf/FCL_simulation_environemnt.pdf', width=12, height=9)
```
Next we plot richness and chain over the environments.
We plot three figures for each definition of FCL
```{r modulater and enviornments}
PlotCumulative =function(df, fname){
  g1=ggplot(df, aes(richness, linetype=factor(resource)))+ stat_ecdf(geom = "step", color='#7570b3')
  g1=g1+xlab('Richness')+ylab('Cumulative Prob.')  
  g1=g1+xlim(c(0, 32))+theme(
  axis.text.x = element_text(size=14),
    axis.title.x = element_text(size=20),
     axis.text.y = element_text(size=14),
    axis.title.y = element_text(size=20),
    legend.position = 'none')+labs(linetype = "Resource")
  
  
  g2=ggplot(df, aes(richness, linetype=factor(disturbance)))+ stat_ecdf(geom = "step", color='#d95f02')
  g2=g2+xlab('Richness')+ylab('Cumulative Prob.')  
  g2=g2+xlim(c(0, 32))+theme(
  axis.text.x = element_text(size=14),
    axis.title.x = element_text(size=20),
     axis.text.y = element_text(size=14),
    axis.title.y = element_text(size=20),
    legend.position = 'none')+labs(linetype = "Disturbance")
  
  g3=ggplot(df, aes(richness, linetype=factor(ecosystem)))+ stat_ecdf(geom = "step", color='#1b9e77')
  g3=g3+xlab('Richness')+ylab('Cumulative Prob.')  
  g3=g3+xlim(c(0, 32))+theme(
  axis.text.x = element_text(size=14),
    axis.title.x = element_text(size=20),
     axis.text.y = element_text(size=14),
    axis.title.y = element_text(size=20),
    legend.position = 'none')+labs(linetype = "Ecosystem")
  
  g4=ggplot(df, aes(chain, linetype=factor(resource)))+ stat_ecdf(geom = "step", color='#7570b3')
  g4=g4+xlab('Chain')+ylab('Cumulative Prob.')  
  g4=g4+xlim(c(0, 1))+theme(
  axis.text.x = element_text(size=14),
    axis.title.x = element_text(size=20),
     axis.text.y = element_text(size=14),
    axis.title.y = element_text(size=20),
    legend.title=element_text(size=20),
  legend.text=element_text(size=14))+labs(linetype = "Resource")
  
  
  g5=ggplot(df, aes(chain, linetype=factor(disturbance)))+ stat_ecdf(geom = "step", color='#d95f02')
  g5=g5+xlab('Chain')+ylab('Cumulative Prob.')  
  g5=g5+xlim(c(0, 1))+theme(
  axis.text.x = element_text(size=14),
    axis.title.x = element_text(size=20),
     axis.text.y = element_text(size=14),
    axis.title.y = element_text(size=20),
    legend.title=element_text(size=20),
  legend.text=element_text(size=14))+labs(linetype = "Disturbance")
  
  g6=ggplot(df, aes(chain, linetype=factor(ecosystem)))+ stat_ecdf(geom = "step", color='#1b9e77')
  g6=g6+xlab('Chain')+ylab('Cumulative Prob.')  
  g6=g6+xlim(c(0, 1))+theme(
  axis.text.x = element_text(size=14),
    axis.title.x = element_text(size=20),
     axis.text.y = element_text(size=14),
    axis.title.y = element_text(size=20),
    legend.title=element_text(size=20),
  legend.text=element_text(size=14))+labs(linetype = "Ecosystem")
  
  g1+g4+g2+g5+g3+g6+plot_layout(nrow = 3,)+plot_annotation(tag_levels = "A")&theme(plot.tag = element_text(size = 32))
  ggsave(paste0('./Simulations/simulation_pdf/', fname), heigh=12, width=12)
}
PlotCumulative(df_long,'Cumulative_richness_chain_FCLlong.pdf')
PlotCumulative(df_mean,'Cumulative_richness_chain_FCLmean.pdf')
PlotCumulative(df_short,'Cumulative_richness_chain_FCLshort.pdf')
```

Below, we plot some additional data.
First, we categorized the ecosystems from the empirical data base.
```{r Ecosystem categories in empirical data}
library(plyr)
df_new=df_emp
C=count(df_emp, 'Ecosystems')
print(C)
# remove categories <=3
remove=C[,2]<=3
remove_category=c()
for (i in 1:length(remove)){
  if(remove[i]==TRUE){
   df_new$Ecosystem[df_new$Ecosystem==C[i,1]]='others' 
  }
}

g1=ggplot(df_new, aes(x=Ecosystem, fill=Ecosystem)) + geom_bar()+ylab('Count')+theme(
  axis.text.x = element_text(size=14, angle=30),
  axis.title.x = element_text(size=24),
   axis.text.y = element_text(size=16),
  axis.title.y = element_text(size=24),
  legend.position="none"
  )
#ggsave("Cohen_Ecosystem_count.pdf")

# calclulate richness and FCLs in each ecosystem
g2=ggplot(data=df_new, aes(x=Ecosystem, y=Richness, color=Ecosystem)) +geom_jitter(position=position_jitter(0.2))+ylab('Richness')+theme(
axis.text.x = element_text(size=14, angle=30),
  axis.title.x = element_text(size=24),
   axis.text.y = element_text(size=16),
  axis.title.y = element_text(size=24),
  )+guides(color = 'none')
#ggsave("Cohen_Ecosystem_richness.pdf")


#ggplot(data=df_new, aes(x=Ecosystem, y=FCL_long, color=Ecosystem)) +geom_jitter(position=position_jitter(0.2))+ylab('FCL long')+theme(
g3=ggplot(df_new, aes(x=Ecosystem, y=FCL_long, color=Ecosystem)) + ylab('FCL long' )+
  geom_count(aes(size=..prop.., group=Ecosystem))+theme(
axis.text.x = element_text(size=14, angle=30),
  axis.title.x = element_text(size=24),
   axis.text.y = element_text(size=16),
  axis.title.y = element_text(size=24),
  )+guides(color = 'none')
#ggsave("Cohen_Ecosystem_long.pdf")



#ggplot(data=df_new, aes(x=Ecosystem, y=FCL_short, color=Ecosystem)) +geom_jitter(position=position_jitter(0.2))+ylab('FCL short')+theme(
g4=ggplot(df_new, aes(x=Ecosystem, y=FCL_short, color=Ecosystem)) + ylab('FCL short')+
  geom_count(aes(size=..prop.., group=Ecosystem))+theme(
axis.text.x = element_text(size=14, angle=30),
  axis.title.x = element_text(size=24),
   axis.text.y = element_text(size=16),
  axis.title.y = element_text(size=24),
  #legend.position="none"
  )+guides(color = 'none')
#ggsave("Cohen_Ecosystem_short.pdf")
g1+g2+g3+g4+plot_layout(nrow = 2)+plot_annotation(tag_levels = "A")&theme(plot.tag = element_text(size = 32))
ggsave('./empirical_pdf/Empirical_SI.pdf', heigh=12, width=12)
```
Next, we plot the cumulative probabilities over the two environmental factors
```{r resource and disturbance}
g1=ggplot(df_long, aes(richness, linetype=factor(resource), color=factor(disturbance)))+ stat_ecdf(geom = "step")
g1=g1+xlab('Richness')+ylab('Cumulative Prob.')  
g1=g1+xlim(c(0, 32))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position = 'none')+labs(linetype = "Resource", color='Disturbance')


g2=ggplot(df_mean, aes(richness, linetype=factor(resource), color=factor(disturbance)))+ stat_ecdf(geom = "step")
g2=g2+xlab('Richness')+ylab('Cumulative Prob.')  
g2=g2+xlim(c(0, 32))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position = 'none')+labs(linetype = "Resource", color='Disturbance')


g3=ggplot(df_short, aes(richness, linetype=factor(resource), color=factor(disturbance)))+ stat_ecdf(geom = "step")
g3=g3+xlab('Richness')+ylab('Cumulative Prob.')  
g3=g3+xlim(c(0, 32))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position = 'none')+labs(linetype = "Resource", color='Disturbance')

g4=ggplot(df_long, aes(chain, linetype=factor(resource), color=factor(disturbance)))+ stat_ecdf(geom = "step")
g4=g4+xlab('Chain')+ylab('Cumulative Prob.')  
g4=g4+xlim(c(0, 1))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20))+labs(linetype = "Resource", color='Disturbance')


g5=ggplot(df_mean, aes(chain, linetype=factor(resource), color=factor(disturbance)))+ stat_ecdf(geom = "step")
g5=g5+xlab('Chain')+ylab('Cumulative Prob.')  
g5=g5+xlim(c(0, 1))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20))+labs(linetype = "Resource", color='Disturbance')

g6=ggplot(df_short, aes(chain, linetype=factor(resource), color=factor(disturbance)))+ stat_ecdf(geom = "step")
g6=g6+xlab('Chain')+ylab('Cumulative Prob.')  
g6=g6+xlim(c(0, 1))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20))+labs(linetype = "Resource", color='Disturbance')

g1+g4+g2+g5+g3+g6+plot_layout(nrow = 3,)+plot_annotation(tag_levels = "A")&theme(plot.tag = element_text(size = 32))
ggsave('./Simulations/simulation_pdf/Cumulative_Richness_Chain_ver1.pdf', heigh=12, width=12)

```

```{r resource and ecosystem}
g1=ggplot(df_long, aes(richness, linetype=factor(resource), color=factor(ecosystem)))+ stat_ecdf(geom = "step")
g1=g1+xlab('Richness')+ylab('Cumulative Prob.')  
g1=g1+xlim(c(0, 32))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position = 'none')+labs(linetype = "Resource", color='Ecosystem')


g2=ggplot(df_mean, aes(richness, linetype=factor(resource), color=factor(ecosystem)))+ stat_ecdf(geom = "step")
g2=g2+xlab('Richness')+ylab('Cumulative Prob.')  
g2=g2+xlim(c(0, 32))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position = 'none')+labs(linetype = "Resource", color='Ecosystem')


g3=ggplot(df_short, aes(richness, linetype=factor(resource), color=factor(ecosystem)))+ stat_ecdf(geom = "step")
g3=g3+xlab('Richness')+ylab('Cumulative Prob.')  
g3=g3+xlim(c(0, 32))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position = 'none')+labs(linetype = "Resource", color='Ecosystem')

g4=ggplot(df_long, aes(chain, linetype=factor(resource), color=factor(ecosystem)))+ stat_ecdf(geom = "step")
g4=g4+xlab('Chain')+ylab('Cumulative Prob.')  
g4=g4+xlim(c(0, 1))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20))+labs(linetype = "Resource", color='Ecosystem')


g5=ggplot(df_mean, aes(chain, linetype=factor(resource), color=factor(ecosystem)))+ stat_ecdf(geom = "step")
g5=g5+xlab('Chain')+ylab('Cumulative Prob.')  
g5=g5+xlim(c(0, 1))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20))+labs(linetype = "Resource", color='Ecosystem')

g6=ggplot(df_short, aes(chain, linetype=factor(resource), color=factor(ecosystem)))+ stat_ecdf(geom = "step")
g6=g6+xlab('Chain')+ylab('Cumulative Prob.')  
g6=g6+xlim(c(0, 1))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20))+labs(linetype = "Resource", color='Ecosystem')

g1+g4+g2+g5+g3+g6+plot_layout(nrow = 3,)+plot_annotation(tag_levels = "A")&theme(plot.tag = element_text(size = 32))
ggsave('./Simulations/simulation_pdf/Cumulative_Richness_Chain_ver2.pdf', heigh=12, width=12)

```

```{r disturbance and ecosystem}
g1=ggplot(df_long, aes(richness, linetype=factor(disturbance), color=factor(ecosystem)))+ stat_ecdf(geom = "step")
g1=g1+xlab('Richness')+ylab('Cumulative Prob.')  
g1=g1+xlim(c(0, 32))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position = 'none')+labs(linetype = "Disturbance", color='Ecosystem')


g2=ggplot(df_mean, aes(richness, linetype=factor(disturbance), color=factor(ecosystem)))+ stat_ecdf(geom = "step")
g2=g2+xlab('Richness')+ylab('Cumulative Prob.')  
g2=g2+xlim(c(0, 32))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position = 'none')+labs(linetype = "Disturbance", color='Ecosystem')


g3=ggplot(df_short, aes(richness, linetype=factor(disturbance), color=factor(ecosystem)))+ stat_ecdf(geom = "step")
g3=g3+xlab('Richness')+ylab('Cumulative Prob.')  
g3=g3+xlim(c(0, 32))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position = 'none')+labs(linetype = "Disturbance", color='Ecosystem')

g4=ggplot(df_long, aes(chain, linetype=factor(disturbance), color=factor(ecosystem)))+ stat_ecdf(geom = "step")
g4=g4+xlab('Chain')+ylab('Cumulative Prob.')  
g4=g4+xlim(c(0, 1))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20))+labs(linetype = "Disturbance", color='Ecosystem')


g5=ggplot(df_mean, aes(chain, linetype=factor(disturbance), color=factor(ecosystem)))+ stat_ecdf(geom = "step")
g5=g5+xlab('Chain')+ylab('Cumulative Prob.')  
g5=g5+xlim(c(0, 1))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20))+labs(linetype = "Disturbance", color='Ecosystem')

g6=ggplot(df_short, aes(chain, linetype=factor(disturbance), color=factor(ecosystem)))+ stat_ecdf(geom = "step")
g6=g6+xlab('Chain')+ylab('Cumulative Prob.')  
g6=g6+xlim(c(0, 1))+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20))+labs(linetype = "Disturbance", color='Ecosystem')

g1+g4+g2+g5+g3+g6+plot_layout(nrow = 3,)+plot_annotation(tag_levels = "A")&theme(plot.tag = element_text(size = 32))
ggsave('./Simulations/simulation_pdf/Cumulative_Richness_Chain_ver3.pdf', heigh=12, width=12)

```
