---
title: "FCL and motif"
output:
  html_document:
    df_print: paged
---

In this notebook, we analyze the relationship between FCL and the fractions of the motives in empirical food webs.
We use igraph package to analyze food webs.
To measure the fractions of the motives we use triad_census function in igraph.
Note that 13 motives are defined but this function returns 16 motives because 
the function can include sub-graphs that include isolated nodes. Such sub-graphs are removed in the analysis.
We use the database from Cohen (2011), whioch contains 213 empirical food webs.

```{r Measure FCL}
library(tidyverse)
library(igraph)
FCL=function(A, def=0){
  # A: an adjacency matrix of directed food web
  # def: definition of FCL. We choose one definition from below
  # def =-1: shortest-path
  # def =0 (default)  mean trophic levels of prey +1. Only acyclic graph
  # def = 1: longest-path. Only acyclic graph
  
  N = nrow(A) # number of species in the food web
  TL=rep(0, N)
  B=c()
  # Check the indexes of basal species
  for (i in 1:N){
    if (sum(A[, i])==0){
      TL[i]=1 # basal species
      B=c(B, i) # list of basal species
    }
  }
  
  # Check whether A is DAG or not
  # calculate trophic levels 
  
  
  for (i in 1:N){
    if(TL[i]==0){
      # analyze nob-basal species
      if (def==0){
          # we define FCL by mean prey's tropic level
          TL[i] = 1+(TL[1:(i-1)]%*%A[1:(i-1), i])/sum(A[1:(i-1), i])
      }
      else if (def==-1){
          # TL of species i is defined by 1+the shortest path from a basal species
          graph=graph_from_adjacency_matrix(A,mode='directed')
          TL[i] = 1+min(distances(graph,to = i, mode='out')[B]) 
      }
      else if (def==1){
          #TL of species i is defined by 1+the longest path from a basal species
          # Because igraph does not have an algorithm for the longest path
          # we will use the shortest path with negative weights
          graph=graph_from_adjacency_matrix(-A,mode='directed', weight=TRUE)
          TL[i] =1- min(distances(graph,to = i, mode='out')[B]) # we only care distances from basal species to species i
      }
    }
  }
 #print(TL)
  return (max(TL)-1) # FCL= max TL -1
}
```

```{r DataFrame Generation}
# define A 

# read from Data base
# NOTE THAT WE NEED TO CHANGE SEPARATOR IN THE FILES
# Unfortunately, we CANNOT define FCL based  on prey's trophic levels 
# because the species's induces are not sorted so that an adj matrix is upper-triangular.
# and because we do not know an algorithm to sort the species induces.
Analysis = function (d){
  # d row csv file
  # return FCLs and number fo the motives
  D=d[, 4:ncol(d)]
  #rownames(D)=d[, 3]
  #colnames(D)=d[1,4:ncol(d) ]
  A=data.frame(D)
  colnames(A)=colnames(D)
  rownames(A)=as.character(unlist(d[, 3]))
  for (i in 1:nrow(A)){
    if (as.integer(rownames(A))[i]<10){
      rownames(A)[i] = paste0("0",rownames(A)[i])
    }
  }
  
  for (i in 1:ncol(A)){
    if (as.integer(colnames(A))[i]<10){
      colnames(A)[i] = paste0("0",colnames(A)[i])
    }
  }
  # We need to convert a data into NxN matrix
  N_list=sort(unique(c(rownames(A), colnames(A)))) # total number of species in the food web
  col_check=!(N_list %in% colnames(A)) # which species is missing in columns?
  row_check=!(N_list %in% rownames(A)) # which species is missing in rows?
  for(i in 1:length(N_list)){
    if (col_check[i]==TRUE){
       add = rep(0, nrow(A))
       a=cbind(A, add)
       #if(i<10){
       #  colnames(a)=c(colnames(A), paste0("0",N_list[0]))
       #}else{
        # colnames(a)=c(colnames(A), paste0(N_list[i]))
       #}
       colnames(a)=c(colnames(A), paste0(N_list[i]))
       A= a %>% select(all_of(names(a) %>% sort())) # update A and sorting
    }
    if (row_check[i]==TRUE){
       add = rep(0, ncol(A))
       a=rbind(A, add)
       #if(i<10){
      #   rownames(a)=c(rownames(A), paste0("0",N_list[i]))
      # }else{
       #  rownames(a)=c(rownames(A), paste0(N_list[i]))
       #}
       rownames(a)=c(rownames(A), paste0(N_list[i]))
       A=a %>% arrange(rownames(a)) # update A and sorting
    }
  } 
  A=matrix(unlist(A), ncol=ncol(A))  # convert matrix so that we can use it in igraph
  graph=graph_from_adjacency_matrix(A,mode='directed')
  if (is.dag(graph)==TRUE){
    #FCL_mean=FCL(A, def=0) # FCL based on mean prey trophic level
    # convert weighted adj into unweighted one
    A =matrix(as.integer(A>0), nrow=nrow(A))
    FCL_long = FCL(A, 1)
  }else{
  # In this case, two FCLs cannot be defined
  #FCL_mean=NaN
  FCL_long=NaN
  # convert weighted adj into unweighted one
  A =matrix(as.integer(A>0), nrow=nrow(A))
  }
  FCL_short =FCL(A, -1) # this can be defined in any food webs. Return Inf without basal species
  
  motif=matrix(triad_census(graph), nrow=1)
  # the names of the motives follow previous studies
  data=data.frame(FCL_short, FCL_long, nrow(A), motif)
  colnames(data) = c('FCL_short', 'FCL_long',"richness", 
                    "empty","monoA-single","bi-single",
                    "s5","s4","s1","d4","d3","s2",
                    "s3","d8","d2","d1","d5","d7","d6")
  return (data)
}

```
```{r Main}
#Main
# Note that we used the cleaned data from the database so that we can easily analyze them in R
# We do not calcualte FCL_mean heere because adj matrix does not necesarily upper-triangular although it is DAG.
for(i in 1:213){
  fname=paste0('./EmpiricalFoodWeb/ECOWeB1.1/DATFILES Predation Matrices/WEB',i,'.DAT')
  d=read_csv(fname)
  if (i==1){
  data=Analysis(d)
  }else{
    data=rbind(data, Analysis(d))
  }
write.csv(data, "Cohen2010_summary.csv", row.names = FALSE)
}
```
Below, we plot distributions of FCLs and richness, and a collaboration matrix.
Some important variables:
s1: chain motif,
s2: omnivory motif,
s3: cyclic predation motif (RSP game)
s4 & 5: apparent or exploitative competition motives (2 prey or 2 predators, respectively)
```{r Data analysis and vizualization}
library(ggplot2)
library(tidyverse)
data=read.csv("Cohen2010_summary.csv") # this csv data summarizes the FCLs and the NUMBERS of fractions

# plot FCLs and richness
ggplot(data, aes(x=FCL_short)) + geom_bar()+xlab('FCL short')+ylab('Count')+ theme(text = element_text(size = 20))   
ggsave('Empirical_FCL_short.pdf')
ggplot(data, aes(x=FCL_long)) + geom_bar()+xlab('FCL long')+ylab('Count')+ theme(text = element_text(size = 20)) 
ggsave('Empirical_FCL_long.pdf')
ggplot(data, aes(x=richness)) + geom_bar()+xlab('Richness')+ylab('Count')+ theme(text = element_text(size = 20)) 
ggsave('Empirical_richness.pdf')
# remove empty, mono- and bi-single as they are not used in previous studies
df = subset(data, select = -c(empty,monoA.single, bi.single) )
df=df %>% select(order(colnames(df)))
df=dplyr::select(df, WEB_id,FCL_long,FCL_short,richness,Ecosystem, everything())
head(df)
# Below we analyze df. We may need to convert the numbers of the motives into their fractions
sum.motif=apply(df[, 6:ncol(df)], 1, sum) # sum of motives in each row
df[, 6:ncol(df)] = df[, 6:ncol(df)]/sum.motif # converting into fractions of motives
# we remove s3 and d5-d8 from the data frame because they  are missing in all data
#print(apply(df[, 4:ncol(df)], 2, sum))
df = subset(df, select = -c(s3, d5, d6, d7,d8) )
df[, 6:ncol(df)] = scale(df[,6:ncol(df)]) # this is scaled data. 
# check correlation
library(ggcorrplot)
corr=cor(subset(df, select=-c(WEB_id, Ecosystem)), use = "pairwise.complete.obs") # pearson and spearman show similar results
ggcorrplot(corr)


```


In the manuscript. we may not need to show the motives of ds.

```{r}
dd=subset(df, select = -c(WEB_id, Ecosystem, d1, d2,d3, d4) )
colnames(dd) = c('FCL long', 'FCL short', 'Richness', 
                 'Chain', 'Omnivory', 'Apparent comp', 'Exploitative comp')
corr=cor(dd, use = "pairwise.complete.obs", method='spearman') # pearson and spearman show similar results
p.mat <- cor_pmat(dd, use = "pairwise.complete.obs",  method='pearson') # p values
ggcorrplot(corr, type = "lower", p.mat = p.mat) + theme(axis.text = element_text(size = 24))     
ggsave("Cohen_correlation.pdf")

# Plot FCL against motives

```
FCL_short is biased toward FCL_short=2 and the variation seems very small, which suggests that the analysis on FCL_short is not promising. IN contrast, FCL_long has a larger variation and we are likely to analyze how the fractions of the motives affect FCL_long. 
In addition, we have a variation in species richness, and we can remove the effect of richness on FCL_long in a stat model.
In the correlation matrix, we can see positive correlations between FCL_long and s1 (chain), s2 (omnivory), and richness. This would be intuitive. In the chain and omnivory motives, FCL_long is two, while FCL_long of competition is one; then, having the chain or omnivory motives would inclurease FCL_long in the whole food web. In addition, if we have more species, we are likely to have longer FCL as the max FCL is richness minus one (when theb whole food web is chain).

Below, we will see some simple linear regressions.
Note that we use the scaled variable so that means of richness and the fractions of the motives are zero while their sds are ones. This enables us to compare their "effects" on FCL_long (although, this is not the causal inference).
```{r Linear regression}
library(car)
print('Shortest path length')
model_short=lm(formula = FCL_short ~ richness + s1 +s4, data = df)
summary(model_short) # we use ds as intercept
vif(model_short)
print('Longest path length')
model_long=lm(formula = FCL_long ~ richness + s1 + s2 + s5, data = df)
summary(model_long) # we use s5 as intercept
vif(model_long)
``` 
As the variations in FCL-short is small, the regression is not interesting as expected. In contrast, we can see the effects of the single-path motives on FCL_long. Let's us see next the comparisons between the prediction and acutual FCL_long.
Note: linear regression would not be a good choice as FCL is discrete. Below we try some glms.

```{r GLM gaussian}
library(ggfortify)
model1=glm(FCL_long~richness+s1+s2+s5, data=df, family = 'gaussian') # gaussian
summary(model1)
autoplot(model1, label.size = 3)

plot(data$FCL_long[-(which(is.na(data$FCL_long)))],predict(model1), 
     xlab='FCL_long', ylab='Prediction 1',
     xlim=c(1,10), ylim=c(1, 10))
par(new=T)
plot(c(1:10), c(1:10), type='l', 
      xlab='FCL_long', ylab='Prediction 1',
     xlim=c(1,10), ylim=c(1, 10))
# In case you want to check VIF, use the codes below
# library(car)
# barplot(vif(model1), main = "VIF Values", horiz = TRUE, col = "steelblue")
 # As we can see, VIFs are small
```
This model cannot predict long (>6) FCL_long
How about Poisson? The mean of FZCL_long is 3.7 and its variance is 2.3, but this faily function cannot generate FCL>3
```{r GLM Poisson}
model2=glm(FCL_long~richness+s1+s2+s5, data=df, family = 'poisson') # poisson
summary(model2)
autoplot(model2, label.size = 3)

plot(data$FCL_long[-(which(is.na(data$FCL_long)))],predict(model2), 
     xlab='FCL_long', ylab='Prediction 2',
     xlim=c(1,10), ylim=c(1, 10))
par(new=T)
plot(c(1:10), c(1:10), type='l', 
      xlab='FCL_long', ylab='Prediction 2',
     xlim=c(1,10), ylim=c(1, 10))


```
Poisson  is worse.

It seems that FCL_long does not fit a gaussian distribution. Then, how about log (FCL_long)? This would be closer to a gaussian distribution.

```{r}
library(tidyverse)
df=mutate(df, log_FCL_long = log(FCL_long))
model3=glm(log_FCL_long~richness+s1+s2+s5, data=df, family = 'gaussian') # gaussian
summary(model3)
autoplot(model3, label.size = 3)

plot(df$log_FCL_long[-(which(is.na(df$log_FCL_long)))],predict(model3), 
     xlab='log(FCL_long)', ylab='Prediction 3',
     xlim=c(1,2.5), ylim=c(1, 2.5))
par(new=T)
plot(c(0:3), c(0:3), type='l', 
      xlab='log(FCL_long)', ylab='Prediction 3',
     xlim=c(1,2.5), ylim=c(1, 2.5))

```


Next we plot the ecosystem types in the database
```{r ecosystem}
library(plyr)
df_new=df
C=count(df, 'Ecosystem')
print(C)
# remove categories <=3
remove=C[,2]<=3
remove_category=c()
for (i in 1:length(remove)){
  if(remove[i]==TRUE){
   df_new$Ecosystem[df_new$Ecosystem==C[i,1]]='others' 
  }
}

ggplot(df_new, aes(x=Ecosystem, fill=Ecosystem)) + geom_bar()+ylab('Count')+theme(
  axis.text.x = element_text(size=14, angle=30),
  axis.title.x = element_text(size=24),
   axis.text.y = element_text(size=16),
  axis.title.y = element_text(size=24),
  legend.position="none"
  )
ggsave("Cohen_Ecosystem_count.pdf")

# calclulate richness and FCLs in each ecosystem
ggplot(data=df_new, aes(x=Ecosystem, y=richness, color=Ecosystem)) +geom_jitter(position=position_jitter(0.2))+ylab('Richness')+theme(
axis.text.x = element_text(size=14, angle=30),
  axis.title.x = element_text(size=24),
   axis.text.y = element_text(size=16),
  axis.title.y = element_text(size=24),
  )+guides(color = 'none')
ggsave("Cohen_Ecosystem_richness.pdf")


#ggplot(data=df_new, aes(x=Ecosystem, y=FCL_long, color=Ecosystem)) +geom_jitter(position=position_jitter(0.2))+ylab('FCL long')+theme(
ggplot(df_new, aes(x=Ecosystem, y=FCL_long, color=Ecosystem)) + ylab('FCL long' )+
  geom_count(aes(size=..prop.., group=Ecosystem))+theme(
axis.text.x = element_text(size=14, angle=30),
  axis.title.x = element_text(size=24),
   axis.text.y = element_text(size=16),
  axis.title.y = element_text(size=24),
  )+guides(color = 'none')
ggsave("Cohen_Ecosystem_long.pdf")



#ggplot(data=df_new, aes(x=Ecosystem, y=FCL_short, color=Ecosystem)) +geom_jitter(position=position_jitter(0.2))+ylab('FCL short')+theme(
ggplot(df_new, aes(x=Ecosystem, y=FCL_short, color=Ecosystem)) + ylab('FCL short')+
  geom_count(aes(size=..prop.., group=Ecosystem))+theme(
axis.text.x = element_text(size=14, angle=30),
  axis.title.x = element_text(size=24),
   axis.text.y = element_text(size=16),
  axis.title.y = element_text(size=24),
  #legend.position="none"
  )+guides(color = 'none')
ggsave("Cohen_Ecosystem_short.pdf")
```


```{r Plo FCL against motives}
library(patchwork)
data=read.csv("Cohen2010_summary.csv") # this csv data summarizes the FCLs and the NUMBERS of fractions
df = subset(data, select = -c(empty,monoA.single, bi.single) )
df=df %>% select(order(colnames(df)))
df=dplyr::select(df, WEB_id,FCL_long,FCL_short,richness,Ecosystem, everything())
sum.motif=apply(df[, 6:ncol(df)], 1, sum) # sum of motives in each row
df[, 6:ncol(df)] = df[, 6:ncol(df)]/sum.motif # converting into fractions of motives
# we remove s3 and d5-d8 from the data frame because they  are missing in all data
#print(apply(df[, 4:ncol(df)], 2, sum))
df = subset(df, select = -c(WEB_id, s3, d1, d2, d3, d4,d5, d6, d7,d8) )
colnames(df) = c('FCL_long', 'FCL_short', 'Richness','Ecosystems',  
                 'Chain', 'Omnivory', 'Apparent', 'Exploitative')
# Note scaling in this case

p1=ggplot(df, aes(x=Chain, y=FCL_long, size=4, alpha=0.5))+geom_point(color='#a6cee3')+ylab('FCL long')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=9, label=paste0('corr.=', round(cor.test(df$FCL_long, df$Chain, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df$FCL_long, df$Chain, method='spearman')$p.value, 3)), size=5)
p2=ggplot(df, aes(x=Omnivory, y=FCL_long, size=4, alpha=0.5))+geom_point(color='#1f78b4')+ylab('FCL long')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )  +xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=9, label=paste0('corr.=', round(cor.test(df$FCL_long, df$Omnivory, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df$FCL_long, df$Omnivory, method='spearman')$p.value, 3)), size=5)
p3=ggplot(df, aes(x=Apparent, y=FCL_long, size=4, alpha=0.5))+geom_point(color='#b2df8a')+ylab('FCL long')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=9, label=paste0('corr.=', round(cor.test(df$FCL_long, df$Apparent, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df$FCL_long, df$Apparent, method='spearman')$p.value, 3)), size=5)
p4=ggplot(df, aes(x=Exploitative, y=FCL_long, size=4, alpha=0.5))+geom_point(color='#33a02c')+ylab('FCL long')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=9, label=paste0('corr.=', round(cor.test(df$FCL_long, df$Exploitative, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df$FCL_long, df$Exploitative, method='spearman')$p.value, 3)), size=5)


p5=ggplot(df, aes(x=Chain, y=FCL_short, size=4, alpha=0.5))+geom_point(color='#a6cee3')+ylab('FCL short')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=3.75, label=paste0('corr.=', round(cor.test(df$FCL_short, df$Chain, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df$FCL_short, df$Chain, method='spearman')$p.value, 3)), size=5)
p6=ggplot(df, aes(x=Omnivory, y=FCL_short, size=4, alpha=0.5))+geom_point(color='#1f78b4')+ylab('FCL short')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )  +xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=3.75, label=paste0('corr.=', round(cor.test(df$FCL_short, df$Omnivory, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df$FCL_short, df$Omnivory, method='spearman')$p.value, 3)), size=5)
p7=ggplot(df, aes(x=Apparent, y=FCL_short, size=4, alpha=0.5))+geom_point(color='#b2df8a')+ylab('FCL short')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=3.75, label=paste0('corr.=', round(cor.test(df$FCL_short, df$Apparent, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df$FCL_short, df$Apparent, method='spearman')$p.value, 3)), size=5)
p8=ggplot(df, aes(x=Exploitative, y=FCL_short, size=4, alpha=0.5))+geom_point(color='#33a02c')+ylab('FCL short')+theme(
axis.text.x = element_text(size=14),
  axis.title.x = element_text(size=20),
   axis.text.y = element_text(size=14),
  axis.title.y = element_text(size=20),
  legend.position="none"
  )+xlim(c(0,1.0))+annotate(geom="text", x=0.4, y=3.75, label=paste0('corr.=', round(cor.test(df$FCL_short, df$Exploitative, method='spearman')$estimate, 3), ', p.val=',  round(cor.test(df$FCL_short, df$Exploitative, method='spearman')$p.value, 3)), size=5)
g=p1+p5+p2+p6+p3+p7+p4+p8+plot_layout(nrow = 4,)+plot_annotation(tag_levels = "A")&theme(plot.tag = element_text(size = 32))

ggsave('FCL_empirical.pdf', width=8, height=12)
```